---
title: "Spanning Trees"
subtitle: "DiscreteMaths.github.io"
output:
  xaringan::moon_reader:
    css: xaringan-themer.css
    lib_dir: libs
    font_size: 20pts
    nature:
      highlightStyle: github
      countIncrementalSlides: false
---

<style type="text/css">
  body{
  font-size: 20pt;
}
</style>

```{r eval=FALSE,include=FALSE}

# CT6 
# - ASI 2005 April Question B - 1
# - ASI 2006 April Question B - 1

```

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(magrittr)
library(knitr)
library(dplyr)
library(janitor)


```

```{r xaringan-themer, include=FALSE, warning=FALSE}
library(xaringanthemer)
style_mono_accent_inverse(
  #base_color = "#4169e1", #)(vvv#TREES
  #background_color = "#E6E6FA",  #TREE
  base_color = "black", #)(
  background_color = "#98a869",
  text_color = "black",
  header_font_google = google_font("Josefin Sans"),
  text_font_google   = google_font("Montserrat", "300", "300i"),
  code_font_google   = google_font("Fira Mono")
)
```

# Hexadecimal Numbers
## Worked Example: Converting Hexadecimal Numbers
<br>
## Discrete Maths for Computer Science Students
<br><br><br><br>
### <tt>DiscreteMaths.github.io</tt>

---

### Exercise 1

Convert the following hexadecimal numbers into their Base 2 equivalents.

A. $5F_{16}$

B. $AE_{16}$

C. $1F_{16}$

D. $B4_{16}$

---

$$\begin{array}{|c||r||c|c|c|} \hline
\text{Decimal} & \text{Binary}  & \text{Hexadecimal} & \text{Octal} & \text{Binary with 4 digits}  \\ 
\text{Base 10} & \text{Base 2} & \text{Base 16} & \text{Base 8} & \text{Base 2} \\ \hline \hline
0 & 0 & 0 & 0 & 0000 \\ \hline
1 & 1 & 1 & 1 & 0001 \\ \hline
2 & 10 & 2 & 2 & 0010 \\ \hline
3 & 11 & 3 & 3 & 0011 \\ \hline
4 & 100 & 4 & 4 & 0100 \\ \hline
5 & 101 & 5 & 5 & 0101 \\ \hline
6 & 110 & 6 & 6 & 0110 \\ \hline
7 & 111 & 7 & 7 & 0111 \\ \hline
8 & 1000 & 8 & 10 & 1000 \\ \hline
9 & 1001 & 9 &11 & 1001 \\ \hline
10 & 1010 & A &12 & 1010 \\ \hline
11 & 1011 & B &13 & 1011 \\ \hline
12 & 1100 & C &14 & 1100 \\ \hline
13 & 1101 & D &15 & 1101 \\ \hline
14 & 1110 & E &16 & 1110 \\ \hline
15 & 1111 & F &17 & 1111 \\ \hline
\end{array}$$


---


### Conversion Steps:
1. Convert each hexadecimal digit to its 4-bit binary equivalent.
2. Combine the binary equivalents to form the full binary number.

#### (A)  $5F_{16}$:
- $5_{16}$ in binary is $0101_2$
- $F_{16}$ in binary is $1111_2$

Combining these:
$$5F_{16} = 0101 1111_2$$

#### (B) $AE_{16}$:
- $A_{16}$ in binary is $1010_2$
- $E_{16}$ in binary is $1110_2$

Combining these:
$$AE_{16} = 1010 1110_2$$

---

#### (C)  $1F_{16}$:
- $1_{16}$ in binary is $0001_2$
- $F_{16}$ in binary is $1111_2$

Combining these:
$$1F_{16} = 0001 1111_2$$

#### (D)  $B4_{16}$:
- $B_{16}$ in binary is $1011_2$
- $4_{16}$ in binary is $0100_2$

Combining these:
$$B4_{16} = 1011 0100_2$$

---

### Summary:

- $5F_{16}$ = $0101 1111_2$

- $AE_{16}$ = $1010 1110_2$

- $1F_{16}$ = $0001 1111_2$

- $B4_{16}$ = $1011 0100_2$


---

### Exercise 2 

Convert the following hexadecimal numbers into their Base 10 equivalents.

A. $91E_{16}$

B. $F32_{16}$

C. $54B_{16}$

D. $79D_{16}$

---

### Conversion Steps:

1. Each digit in the hexadecimal number is multiplied by 16 raised to the power of its position (starting from 0).

2. Sum all the results to get the decimal equivalent.

#### (A)  $91E_{16}$:

$$
9 \times 16^2 + 1 \times 16^1 + E \times 16^0
$$

Here, $E$ in hexadecimal is $14$ in decimal:

$$
9 \times 256 + 1 \times 16 + 14 \times 1 = 2304 + 16 + 14 = 2334
$$

So,

$$91E_{16} = 2334_{10}$$

---

#### (B) $F32_{16}$:

$$
F \times 16^2 + 3 \times 16^1 + 2 \times 16^0
$$

Here, $F$ in hexadecimal is $15$ in decimal:

$$
15 \times 256 + 3 \times 16 + 2 \times 1 = 3840 + 48 + 2 = 3890
$$

So,
$$F32_{16} = 3890_{10}$$

---

#### (C)  $54B_{16}$:

$$
5 \times 16^2 + 4 \times 16^1 + B \times 16^0
$$

Here, $B$ in hexadecimal is $11$ in decimal:

$$
5 \times 256 + 4 \times 16 + 11 \times 1 = 1280 + 64 + 11 = 1355
$$

So,
$$54B_{16} = 1355_{10}$$

#### (D)  $79D_{16}$:

$$
7 \times 16^2 + 9 \times 16^1 + D \times 16^0
$$

Here, $D$ in hexadecimal is $13$ in decimal:

$$
7 \times 256 + 9 \times 16 + 13 \times 1 = 1792 + 144 + 13 = 1949
$$

So,
$$79D_{16} = 1949_{10}$$

---

### Summary:

- $91E_{16}$ = $2334_{10}$

- $F32_{16}$ = $3890_{10}$

- $54B_{16}$ = $1355_{10}$

- $79D_{16}$ = $1949_{10}$
---

---