---
title: "Spanning Trees"
subtitle: "DiscreteMaths.github.io"
output:
  xaringan::moon_reader:
    css: xaringan-themer.css
    lib_dir: libs
    font_size: 20pts
    nature:
      highlightStyle: github
      countIncrementalSlides: false
---

<style type="text/css">
  body{
  font-size: 20pt;
}
</style>

```{r eval=FALSE,include=FALSE}

# CT6 
# - ASI 2005 April Question B - 1
# - ASI 2006 April Question B - 1

```

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(magrittr)
library(knitr)
library(dplyr)
library(janitor)


```

```{r xaringan-themer, include=FALSE, warning=FALSE}
library(xaringanthemer)
style_mono_accent_inverse(
  #base_color = "#4169e1", #)(vvv#TREES
  #background_color = "#E6E6FA",  #TREE
  base_color = "black", #)(
  background_color =  "#D2F0FA",
  text_color="black",
  text_bold_color = "black",
  header_font_google = google_font("Josefin Sans"),
  text_font_google   = google_font("Montserrat", "400", "300i"),
  code_font_google   = google_font("Fira Mono")
)
```
<style> 
  /* Hide page numbers */ .
  remark-slide-number { display: none; } 
</style>

# Graph Theory
## Complete Graphs - Worked Example

<br>
## Discrete Maths for Computer Science Students
<br><br><br><br>
### <tt>DiscreteMaths.github.io</tt>

---

### Objective

This exercise tests your understanding of graph properties, specifically connectivity, completeness, and the existence of Euler trails, Euler circuits, Hamiltonian paths, and Hamiltonian cycles. 

---
### Part A:
1. Given the graph \(G\) with vertices \(V = \{1, 2, 3, 4, 5, 6\}\), draw the graph of the following adjacency matrix:


$$\begin{array}{c||cccccc} & 1 & 2 & 3 & 4 & 5 & 6 \\ \hline \hline 1 & 0 & 1 & 0 & 1 & 0 & 1 \\ 2 & 1 & 0 & 1 & 0 & 1 & 0 \\ 3 & 0 & 1 & 0 & 1 & 0 & 1 \\ 4 & 1 & 0 & 1 & 0 & 1 & 0 \\ 5 & 0 & 1 & 0 & 1 & 0 & 1 \\ 6 & 1 & 0 & 1 & 0 & 1 & 0 \\ \end{array}$$
<ol start="2">
<li>Is the graph connected?</li>
<li>Is the graph complete?</li>
</ol>
---

### Part B:
Does the graph have:
4. an Euler trail?
5. an Euler circuit?
6. a Hamiltonian path?
7. a Hamiltonian cycle?



---

### Part A: 
**Drawing the Graph and Analyzing Connectivity and Completeness**

Given the adjacency matrix:
```
     1 2 3 4 5 6
 1 [ 0 1 0 1 0 1 ]
 2 [ 1 0 1 0 1 0 ]
 3 [ 0 1 0 1 0 1 ]
 4 [ 1 0 1 0 1 0 ]
 5 [ 0 1 0 1 0 1 ]
 6 [ 1 0 1 0 1 0 ]
```

#### Drawing the Graph:
- Vertex 1 is connected to vertices 2, 4, and 6.
- Vertex 2 is connected to vertices 1, 3, and 5.
- Vertex 3 is connected to vertices 2, 4, and 6.
- Vertex 4 is connected to vertices 1, 3, and 5.
- Vertex 5 is connected to vertices 2, 4, and 6.
- Vertex 6 is connected to vertices 1, 3, and 5.

---

### Remark:

* This is a complete bipartite graph and is denoted $K_{3,3}$. 
 
* The graph is connected since each vertex in {1,3,5} is connected to each vertex in {2,4,6}, so there is a path between each pair of vertices in the graph. 
 
---

The graph will look like this:



```{r graph, echo=FALSE,message=FALSE,warning=FALSE}
#install.packages("igraph")
library(igraph)

# Adjacency matrix
adj_matrix <- matrix(
  c(0, 1, 0, 1, 0, 1,
    1, 0, 1, 0, 1, 0,
    0, 1, 0, 1, 0, 1,
    1, 0, 1, 0, 1, 0,
    0, 1, 0, 1, 0, 1,
    1, 0, 1, 0, 1, 0),
  nrow = 6, byrow = TRUE
)

# Create a graph from the adjacency matrix
g <- graph_from_adjacency_matrix(adj_matrix, mode = "undirected")

# Plot the graph
plot(g)

```


---
### Part A: 

**Checking for Connectedness and Completeness**


#### Analysis:
- **Exercise 2: Is the graph connected?** 
  - Yes, the graph is connected because there is a path between any pair of vertices.

- **Exercise 3: Is the graph complete?**
  - No, the graph is not complete because not every pair of vertices is connected by an edge. 
  - In a complete graph with 6 vertices, every vertex should be connected to every other vertex.

---

### Part B: 

**Checking for Euler and Hamiltonian Properties**

#### 1. Does the graph have an Euler trail?
- An Euler trail exists if and only if exactly two vertices have an odd degree (number of edges). 
- Here, each vertex has a degree of 3 (odd degree). Since we have more than two vertices with an odd degree, the graph does not have an Euler trail.

#### 2. Does the graph have an Euler circuit?
- An Euler circuit exists if and only if all vertices have an even degree. 
- In this graph, all vertices have an odd degree, so there is no Euler circuit.


---

### Part B: 

**Checking for Euler and Hamiltonian Properties**


#### 3. Does the graph have a Hamiltonian path?
- A Hamiltonian path is a path that visits each vertex exactly once. 
- Given the symmetry and the connectivity of the graph, there is a Hamiltonian path. 
- For example, one such path could be: 1-2-3-4-5-6.

#### 4. Does the graph have a Hamiltonian cycle?
- A Hamiltonian cycle is a cycle that visits each vertex exactly once and returns to the starting vertex. 
- The graph has a Hamiltonian cycle. 
- One example could be: 1-2-3-4-5-6-1.

---

---
