---
title: "Discrete Mathematics"
output: 
  flexdashboard::flex_dashboard:
    theme: united
    css: style.css
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

```


Discrete Mathematics {data-navmenu="Introduction"}
=====================================

Column {.tabset}
--------------------

### Contents

|| Section | Conponents ||
|--------|:-----:|:---------------------|----------|
| | **Section 1**| Introduction to Numbers and Numbers Systems,  | |
| | **Section 2**| Binary Numbers, Hexadecimal Numbers, Octal Numbers | |
| | **Section 3**| <a href="Section3.html"> Set Theory</a> ||
| | **Section 4**| <a href="Section4.html"> Logic & Logic Networks </a> ||
| | **Section 5**| Functions 1: Mathematical Functions, | |
| | **Section 6**| Functions 2: Invertible Functions & O-Notation| |
| | **Section 7**| <a href="Section7.html">Graph Theory, Trees, Binary Search Trees</a>| |
| | **Section 8**| <a href="Section8.html">Digraphs and Relations</a>| |
| | **Section 9**| <a href="Section9.html">Sequences and Series, with Telescoping Series</a> ||
| | **Section 10**| <a href="Section10.html">Proof by Induction, Convergence and Ratio Tests</a>||
| | **Section 11**| <a href="Section11.html"> Probability and Counting Problems</a>||
| | **Section 12**| <a href="Section12.html"> Matrices and  Systems of Linear Equations</a> ||

### Discrete mathematics


Discrete mathematics is the common name for the fields of mathematics most generally useful in theoretical computer science. This includes computability theory, computational complexity theory, and information theory. 

*  **Computability theory** examines the limitations of various theoretical models of the computer, including the most powerful known model - the Turing machine. 

*  **Complexity theory** is the study of tractability by computer; some problems, although theoretically soluble by computer, are so expensive in terms of time or space that solving them is likely to remain practically unfeasible, even with rapid advance of computer hardware. 

*  Finally, **information theory** is concerned with the amount of data that can be stored on a given medium, and hence concepts such as compression and entropy.

```{r child="sourcefiles/Numbers-IntroductionToNumbers.Rmd"}
```


### Part 1. Number Bases

*  Numbers in Base 10
*  The binary system
*  Calculating in the binary system
*  The Hexadecimal system
*  Converting decimal integers into other bases


### Part 2. Rational Numbers

*  Factor, multiples and primes
*  Representing fractions
*  Decimal fractions
*  Fractions in bases other than 10


### Part 3. Real Numbers

*  Irrational numbers
*  Inequality symbols
*  Floating-point notation


* <a href="https://www.youtube.com/watch?v=/9NAmHx3pAxk" >Number Sets: Natural Numbers, Integers, Rational Numbers and Real Numbers.</a>
* <a href="https://www.youtube.com/watch?v=/lu7uhe903TY" >Irrational Numbers: Exercise involving irrational numbers.</a>
* <a href="https://www.youtube.com/watch?v=/WnXnVADCXuQ" >Rational and Irrational Numbers</a>

* <a href="https://www.youtube.com/watch?v=/mhHAJOQQ8kM" >Repeating Decimals</a>
* <a href="https://www.youtube.com/watch?v=/99qV28WmzH4" >Repeating Decimals</a>
* <a href="https://www.youtube.com/watch?v=/sIowD1XjFJ8" >Repeating Decimals</a>

```{r child="sourcefiles/Numbers-BinaryNumbers.Rmd"}
```

```{r child="sourcefiles/Numbers-Hexadecimal.Rmd"}
```

```{r child="sourcefiles/Numbers-ConversionTable.Rmd"}
```

```{r child="sourcefiles/Numbers-Otherbases.Rmd"}
```

```{r child="TutorialSheets/Numbers-Tutorial-1.Rmd"}
```


```{r child="TutorialSheets/Set-Theory-Tutorial-1.Rmd"}
```



Functions {data-navmenu="Section 3"}
=====================================

Column {.tabset}
-------------------------------------------------

### Functions

* <a href ="https://www.youtube.com/watch?v=/-3hd821alPI">Functions (2005 Q4 Part A)  </a>
* <a href ="https://www.youtube.com/watch?v=/cR5b2zWOa0w">Functions (2003 Q4 Part B) </a>
* <a href ="https://www.youtube.com/watch?v=/IXs5CTQnBU4">Floor Functions Exercise HD	</a>



### Cartesian Product

$X \times Y$

$X = \{1,2,3\}$

$Y = \{a,b,c\}$


$X \times Y = \{ (1,a) , (1,b) , (1,c) , (2,a), (2,b) ,(2,c), (3,a),(3,b),(3,c) \}$ 
$Y \times X = \{ (a,1) , (a,2) , (a,3) , (b,1), (b,2) ,(b,3), (c,1),(c,2),(c,3) \}$ 

 
```{r child="sourcefiles/Functions-MathsFunctions.Rmd"}
```


Invertible Functions {data-navmenu="Section 3"}
=====================================

Column {.tabset}
-------------------------------------------------

### Invertible Functions

Necessary Conditions for Invertibility of a Function

* The function must be one-to-one
* The fucntion must be onto.




* A function is ***onto*** if is range is equal to its codomain.

* A function is ***one-to-one*** if no two distinct elements of the domain have the same image.


```{r child="sourcefiles/Functions-O-Notation.Rmd"}
```

```{r child="TutorialSheets/Functions-Tutorial-1.Rmd"}
```





```{r child="sourcefiles/Graphs-BinarySearchTrees.Rmd"}
```


