---
title: "Discrete Mathematics"
output: 
  flexdashboard::flex_dashboard:
    theme: united
    css: style.css
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

```


Discrete Mathematics {data-navmenu="Introduction"}
=====================================

Column {.tabset}
--------------------

### Contents

|| Section | Conponents ||
|--------|:-----:|:---------------------|----------|
| | **Section 1**| <a href="Section1.html"> Introduction to Numbers and Numbers Systems</a>  | |
| | **Section 2**| <a href="Section2.html"> Binary Numbers, Hexadecimal Numbers, Octal Numbers </a> | |
| | **Section 3**| <a href="Section3.html"> Set Theory</a> ||
| | **Section 4**| <a href="Section4.html"> Logic & Logic Networks </a> ||
| | **Section 5**| <a href="Section5.html"> Functions 1: Mathematical Functions </a> | |
| | **Section 6**| <a href="Section6.html"> Functions 2: Invertible Functions </a>| |
| | **Section 7**| <a href="Section7.html"> Functions 3: O-Notation </a>| |
| | **Section 8**| <a href="Section8.html"> Graph Theory</a>| |
| | **Section 9**| <a href="Section9.html"> Trees, Binary Search Trees</a>||
| | **Section 10**| <a href="Section10.html">Digraphs and Relation</a> ||
| | **Section 11**| <a href="Section11.html">Sequences and Series, with Telescoping Series</a> ||
| | **Section 12**| <a href="Section12.html">Proof by Induction, Convergence and Ratio Tests</a>||
| | **Section 13**| <a href="Section13.html">Probability and Counting Problems</a>||
| | **Section 14**| <a href="Section14.html">Matrices and  Systems of Linear Equations</a> ||


### Discrete mathematics

<h3>Discrete Maths</h3>
Discrete mathematics is the common name for the fields of mathematics most generally useful in theoretical computer science. This includes computability theory, computational complexity theory, and information theory. 

*  **Computability theory** examines the limitations of various theoretical models of the computer, including the most powerful known model 
- the Turing machine. 

*  **Complexity theory** is the study of tractability by computer; some problems, although theoretically soluble by computer, are so expensive in terms of time or space that solving them is likely to remain practically unfeasible, even with rapid advance of computer hardware. 

*  Finally, **information theory** is concerned with the amount of data that can be stored on a given medium, and hence concepts such as compression and entropy.



### Syllabus

```{r child = "Syllabus.Rmd"}
```


