---
title: "Discrete Mathematics"
output: 
  flexdashboard::flex_dashboard:
    theme: united
    css: style.css
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

```


Discrete Mathematics {data-navmenu="Introduction"}
=====================================

Column 
--------------------

### Introduction


#### Discrete mathematics


Discrete mathematics is the common name for the fields of mathematics most generally useful in theoretical computer science. This includes computability theory, computational complexity theory, and information theory. 

*  \textbf{Computability theory} examines the limitations of various theoretical models of the computer, including the most powerful known model - the Turing machine. 

*  \textbf{Complexity theory} is the study of tractability by computer; some problems, although theoretically soluble by computer, are so expensive in terms of time or space that solving them is likely to remain practically unfeasible, even with rapid advance of computer hardware. 

*  Finally, \textbf{information theory} is concerned with the amount of data that can be stored on a given medium, and hence concepts such as compression and entropy.


As a relatively new field, discrete mathematics has a number of fundamental open problems. The most famous of these is the "\textbf{P=NP?}" problem, one of the Millennium Prize Problems. It is widely believed that the answer to this problem is no.




Number Systems {data-navmenu="Section 1"}
==============================================================

Column {.tabset}
-------------------------------------------------------------

### Real and Irrational Numbers

In mathematics, an irrational number is a real number that cannot be expressed as a ratio of integers, i.e. as a fraction. 
Therefore, irrational numbers, when written as decimal numbers, do not terminate, nor do they repeat.


#### Rational and Irrational Numbers
You can tell if it is Rational or Irrational by trying to write the number as a simple fraction.

*  1.5 is rational, because it can be written as the ratio 3/2
*  7 is rational, because it can be written as the ratio 7/1
*  0.333... (3 repeating) is also rational, because it can be written as the ratio 1/3



#### Significant Digits
There are three rules on determining how many significant figures are in a number: Non-zero digits are always significant. Any zeros between two significant digits are significant. A final zero or trailing zeros in the decimal portion ONLY are significant.




#### Floating Point Notation



In computing, floating point describes a method of 
representing an approximation of a real number in a 
way that can support a wide range of values. 


The numbers are, in general, represented approximately 
to a fixed number of significant digits (the mantissa) and scaled using an exponent. 

In essence, computers are integer machines and are capable of representing real numbers only by using complex codes. The most popular code for representing real numbers is called the IEEE Floating-Point Standard .
The term floating point is derived from the fact that there is no fixed number of digits before and after the decimal point; that is, the decimal point can float. There are also representations in 
which the number of digits before and after the decimal point is set, called fixed-point representations. In general, floating-point representations are slower and less accurate than fixed-point representations, but they can handle a larger range of numbers.





### Natural, Rational and Real Numbers

* $\mathbb{N}$ : natural numbers (or positive integers) $\{1,2,3,\ldots\}$
* $\mathbb{Z}$ : integers $\{-3,-2,-1,0,1,2,3,\ldots\}$
\begin{itemize}
* (The letter $\mathbb{Z}$ comes from the word \emph{Zahlen} which means ``numbers" in German.)

* $\mathbb{Q}$ : rational numbers
* $\mathbb{R}$ : real numbers
* $\mathbb{N} \subseteq \mathbb{Z } \subseteq \mathbb{Q} \subseteq \mathbb{R}$

* (All natural numbers are integers. All integers are rational numbers. All rational numbers are real numbers.)



### Irrational Numbers

An irrational number cannot be expressed as a ratio between two numbers and it cannot be written as a simple fraction because there is not a finite number of numbers when written as a decimal. Instead, the numbers in the decimal would go on forever, without repeating.




#### Real and Irrational Numbers

*  <a title="Number Sets" href="http://youtu.be/9NAmHx3pAxk" >Number Sets</a>Natural Numbers, Integers, Rational Numbers and Real Numbers.
*  <a title="Irrational Numbers" href="http://youtu.be/lu7uhe903TY" >Irrational Numbers</a>: Exercise involving irrational numbers.
*  <a title="Rational Numbers" href="http://youtu.be/WnXnVADCXuQ" >Rational and Irrational Numbers</a>[4:16] (New Video)
*  <a title="Repeating Decimals" href="http://youtu.be/mhHAJOQQ8kM" >Repeating Decimals</a>(video 1)
*  <a title="Repeating Decimal" href="http://youtu.be/99qV28WmzH4" >Repeating Decimal </a>[3:37](Video 2)


<h5>Discrete Maths: Numbers</h5>


### Part 1. Number Bases

*  Numbers in Base 10
*  The binary system
*  Calculating in the binary system
*  The Hexadecimal system
*  Converting decimal integers into other bases


### Part 2. Rational Numbers

*  Factor, multiples and primes
*  Representing fractions
*  Decimal fractions
*  Fractions in bases other than 10


### Part 3. Real Numbers

*  Irrational numbers
*  Inequality symbols
*  Floating-point notation


* <a href="https://www.youtube.com/watch?v=/9NAmHx3pAxk" >Number Sets: Natural Numbers, Integers, Rational Numbers and Real Numbers.</a>
* <a href="https://www.youtube.com/watch?v=/lu7uhe903TY" >Irrational Numbers: Exercise involving irrational numbers.</a>
* <a href="https://www.youtube.com/watch?v=/WnXnVADCXuQ" >Rational and Irrational Numbers</a>

* <a href="https://www.youtube.com/watch?v=/mhHAJOQQ8kM" >Repeating Decimals</a>
* <a href="https://www.youtube.com/watch?v=/99qV28WmzH4" >Repeating Decimals</a>
* <a href="https://www.youtube.com/watch?v=/sIowD1XjFJ8" >Repeating Decimals</a>



Binary Numbers {data-navmenu="Section 1"}
==================================

* <a href="https://www.youtube.com/watch?v=/Xj75KbggKMU">Binary Number Conversion</a>

* <a href="https://www.youtube.com/watch?v=/xyo2UiDpND8"> Expressing Binary Numbers</a>

* <a href="https://www.youtube.com/watch?v=/HDQ7PGYo5Y8"> Binary Addition</a>

* <a href="https://www.youtube.com/watch?v=/Hz3PfnllV6I">Binary Addition</a>

* <a href="https://www.youtube.com/watch?v=/cnv7scvjc7o"> Binary Addition </a>

* <a href="https://www.youtube.com/watch?v=/dQMQMvU4GT0"> Binary Subtraction: using Borrowing Method</a>

* <a href="https://www.youtube.com/watch?v=/iwzaZDdaT9g">Binary Numbers Adding Two Binary Numbers (Example) HD</a>
    
* <a href="https://www.youtube.com/watch?v=/DTO3mS5D2lA">Binary Subtraction using "Two's Complement"</a>

* <a href="https://www.youtube.com/watch?v=/Ai5F0KLyh2Q"> Left Shifting Technique for Binary Multiplication</a>

* <a href="https://www.youtube.com/watch?v=/P_vd1vkafYk">  Binary Subtraction: using Twos Complement</a>
    
* <a href="https://www.youtube.com/watch?v=/WfWHdWwITgk"> Binary Multiplication: using Left Shifting</a>

* <a href="https://www.youtube.com/watch?v=/A08P9ZJsLOs"> Relations -Example</a>

* <a href="https://www.youtube.com/watch?v=/-svSPXMGyfs "> Binary Multiplication ( Binary Numbers Tutorial Sheet)		</a>


Column {.tabset}
-----------------------------

```{r child="sourcefiles/Numbers-Hexadecimal.Rmd"}
```

Set Theory {data-navmenu="Section 2"}
====================================

Column {.tabset}
-------------------------------------------------------------

### Set Theory Operations

*  The Universal Set $\mathcal{U}$
*  Union
*  Intersection
*  Set Difference
*  Relative Difference


### Set Specification



NOTATIONS FOR A SET:

A set can be represented by two methods:
1.	ROSTER METHOD
2.	BUILDER METHOD
ROSTER METHOD:

In this method the elements of a set are separated by commas and are enclosed within curly brackets { }. For example:

A = {1, 2, 3, 4, 5, 6} is a set of numbers.

B = {Sunny, Joy, Kartik, Harish, Girish} is a set of names.

C = {a, e, i, o, u} is a set of vowels.

D = {apple, banana, guava, orange, pear} is a set of fruits.

Listing the elements in this way is called Roster method. In this method, it is not necessary for the elements to be listed in a particular order. The elements of the set can be written just plainly, separated by commas and in any order.


#### BUILDER METHOD:

This method is also called Property method. In Builder method, a set is represented by stating all the properties which are satisfied by the elements of that particular set only.

For example:

If A is a set of elements less than 0, then in Builder method it will be written as

A = {x: x < 0}, this statement is read as "the set of all x such that x is less than 0"

If A is a set of all real numbers less than 7, then in Builder method it is written as A = {x   R: x < 7}

Similarly,

A = {2i: i is an integer} is a set of all even integers.

A = {x   R: x ? 2} is a set of all real numbers except 2.

A = {x   R: x > 3 and x < 7} is a set of real numbers greater than 3 but less than 7.

A = {x   Z: x > 6} is a set of integers greater than 6.

A = {x   Z: 2x + 1} is a set of all odd integers.

### Set theory

#### Definition of a set

A set is defined completely by its elements. Formally, sets X and Y are the same set if they have the same elements; that is, if every element of X is also an element of Y, and vice versa. For example, suppose we define:

\[ F = \{x | \mbox{(x is an integer)} \mbox{ and } 0 < x < 4)\}  \]
%Then F=A. The definition also makes it clear that {1,2,3} = (3,2,1} = {1,1,2,3,2}. Note also that if X and Y are both empty, then they are equal, justifying referring to "the" empty set.

The equivalence of empty sets has a \textbf{\textit{metaphysical}} consequence for some theories of the metaphysics of properties that define the property of being x as simply the set of all x, then if the two properties are uninstantiated or coextensive they are equivalent - under this theory, because there are no unicorns and there are no pixies, the property of being a unicorn and being a pixie are the same - but if there were a unicorns and pixies, we could tell them apart. (See Universals for more on this.)

### Elements and subsets}

The $\in$  sign indicates set membership. If x is an element (or "member") of a set X, we write $ \in X$; e.g. $3\in A$. (We may also say ``X contains x" and ``A contains 3")

A very important notion is that of a subset. X is a subset of Y, written $X \subseteq Y$ (sometimes simply as$X \subset Y$), if every element of X is also an element of Y. From before $C\subseteq A \subseteq E$.
\subsection{Sets containing Sets}


Sets can of course be elements of other sets; for example we can form the set $G = \{A,B,C,D,E\}$, whose five elements are the sets we considered earlier. Then, for instance, $A\in G$. (Note that this is very different from saying $A\subseteq G$)

%The tilde (~) is as usual used for negation; e.g. $\tilde(A\in B)$.







### Number Sets

The font that the symbols are written in (i.e. $\mathbb{N}$, $\mathbb{R}$) is known as \textit{\textbf{blackboard font}}.
\begin{itemize}
*  $\mathbb{N}$ Natural Numbers ($0,1,2,3$) 
(Not used in the CIS102 Syllabus)
*  $\mathbb{Z}$ Integers ($-3,-2,-1,0,1,2,3, \ldots$)
\begin{itemize}
* [$\ast$] $\mathbb{Z}^{+}$ Positive Integers
* [$\ast$] $\mathbb{Z}^{-}$ Negative Integers
\end{itemize}
*  $\mathbb{Q}$ Rational Numbers
*  $\mathbb{R}$ Real Numbers
\end{itemize}


#### Sets of Numbers

*  $\mathbb{Z}$ Set of all integers
*  $\mathbb{Q}$ Set of all rational numbers
*  $\mathbb{R}$ Set of all real numbers


*  $\mathbb{Z}^{+}$ Set of all positive integers
*  $\mathbb{Z}^{-}$ Set of all negative integers
*  $\mathbb{R}^{+}$ Set of all positive real numbers
*  $\mathbb{R}^{-}$ Set of all negative real numbers

### Power set

The power set of X, $P(X)$, is the set whose elements are all the subsets of X. Thus \[P(A) = \{ \{\}, \{1\}, \{2\}, \{3\}, \{1,2\}, \{1,3\}, \{2,3\}, \{1,2,3\}\}\]. The power set of the empty set $P(\{\})$ = $\{\{\}\}$. 

Note that in both cases the cardinality of the power set is strictly greater than that of base set: No one-to-one correspondence exists between the set and its power set. 

%Cantor proved that this in fact holds for any set (Cantor's Theorem). This is obvious for a finite set, but Cantor's ingenious proof made no reference to the set being finite; the theorem holds even for infinite sets. This was a powerful generalisation of his previous discovery that different sizes of infinity exist.




```{r child="sourcefiles/Logic-IntroductionToLogic.Rmd"}
```

Functions {data-navmenu="Section 3"}
=====================================

Column {.tabset}
-------------------------------------------------
### Functions

* <a href ="https://www.youtube.com/watch?v=/-3hd821alPI">Functions (2005 Q4 Part A)  </a>
* <a href ="https://www.youtube.com/watch?v=/cR5b2zWOa0w">Functions (2003 Q4 Part B) </a>
* <a href ="https://www.youtube.com/watch?v=/IXs5CTQnBU4">Floor Functions Exercise HD	</a>

### Invertible Functions

Necessary Condtions for Invertibility of a Function

* The function must be one-to-one
* The fucntion must be onto.

 
Mathematical Functions{data-navmenu="Section 3"}
=====================================

Column {.tabset}
-------------------------------------------------

### Logarithms

### Exponennts

### Absolute Value, Sign

\subsection*{Absolute Value Function (4.1.3)}


*  The absolute value of some real number $x$ is denoted $|x|$.
*  If the number is positive, the asbolute value is the same number.
*  If the number is negative, the asbolute value is the number without the minus sign.
*  $|2|=2$
*  $|-2| = 2$


### Tutorial


Invertible Functions {data-navmenu="Section 3"}
=====================================

Column {.tabset}
-------------------------------------------------

### Invertible Functions







```{r child="sourcefiles/Graphs-IntroductionToGraphs.Rmd"}
```

```{r child="sourcefiles/Graphs-Trees.Rmd"}
```

Relations and Digraphs {data-navmenu="Section 4"}
=====================================



Column {.tabset}
-------------------------------------------------

#### Digraphs and Relations

### Relations

* A relation $R$ from a set A to a set B is a subset of the
\textbf{cartesian product} A x B. 
* Thus R is a set of \textbf{ordered pairs} where
the first element comes from A and the second element comes
from B i.e. $(a, b)$

* If $(a, b) \in R$ we say that $a$ is related to $b$ and write $aRb$.
* If $(a, b) \notin R$, we say that $a$ is not related to $b$ and write $aRb$. CHECK
* If $R$ is a relation from a set $A$ to itself then we say that ``$R$ is a relation
on $A$".


### Videos 

* < a href = ="https://www.youtube.com/watch?v=/4vSr6q5Nxqc"> Digraphs and Relations</a>

*  < a href = ="https://www.youtube.com/watch?v=/dHzu897SdDA">  Cartesian Products</a>

*  < a href = ="https://www.youtube.com/watch?v=/4vSr6q5Nxqc">  Digraphs and Relations -Example</a>

* < a href = ="https://www.youtube.com/watch?v=/eZIEc1O0W1w"> Relations Example 2</a>

*  < a href = ="https://www.youtube.com/watch?v=/dHzu897SdDA">  Cartesian </a>

*  < a href = ="https://www.youtube.com/watch?v=/4vSr6q5Nxqc">  Digraphs and Relations -Example</a>

* < a href = ="https://www.youtube.com/watch?v=/rG8mhlqnkr0">  Relations -Example</a>

*  < a href = ="https://www.youtube.com/watch?v=/_QTKlTJYKRA">  Transitive Relations</a>

*  < a href = ="https://www.youtube.com/watch?v=/A08P9ZJsLOs">  Relations -Example</a>




### Room 3

<h5>Building smarter solutions with no expertise in machine learning (Laurent Picard)</h5>



```{r child="sourcefiles/SequenceSeries-IntroductionToSequencesSeries.Rmd"}
```

Finite Series {data-navmenu="Section 5"}
=====================================

Column {.tabset}
-------------------------------------------------


### Finite Series and Sigma Notation
Mathematical notation uses a symbol that compactly represents summation of many similar terms: the summation symbol, $\sum$, an enlarged form of the upright capital Greek letter *Sigma*. 

This is defined as:
\[\sum_{i=m}^n a_i = a_m + a_{m+1} + a_{m+2} +\cdots+ a_{n-1} + a_n. \]
Where, i represents the index of summation; ai is an indexed variable representing each successive term in the series; m is the lower bound of summation, and n is the upper bound of summation. The "i = m" under the summation symbol means that the index i starts out equal to m. The index, i, is incremented by 1 for each successive term, stopping when i = n.
Here is an example showing the summation of exponential terms (all terms to the power of 2):
\[\sum_{i=3}^6 i^2 = 3^2+4^2+5^2+6^2 = 86.\]
Informal writing sometimes omits the definition of the index and bounds of summation when these are clear from context, as in:
\[\sum a_i^2 = \sum_{i=1}^n a_i^2.\]


#### Three Important Summation Identities
(index term = i , Number of terms = n }


*  Identity 1
\[ \sum^{i=n}_{i=1} 1 = n \]
*  Identity 2  
\[ \sum^{i=n}_{i=1} i = \frac{n(n+1)}{2} \]
*  Identity 3 
\[ \sum^{i=n}_{i=1} i^2 = \frac{(2n+1)(n+1)(n)}{6} \]


### Partitioning of Summations 


For some integers $m$ and $n$, with $m<n$.

\[ \sum^{i=n}_{i=1} u_{i} = \sum^{i=m}_{i=1} u_{i} + \sum^{i=n}_{i=m+1} u_{i}\]

Suppose $n=100$ and $m=50$

\[ \sum^{i=100}_{i=1} u_{i} = \sum^{i=50}_{i=1} u_{i} + \sum^{i=100}_{i=51} u_{i}\]

\textbf{Example}
Evaluate the following expression:
\[ \sum^{i=100}_{i=51} (i+1) \]


***Step 1*** Evaluate this expression using the identities (notice the lower bound)
\[ \sum^{i=100}_{i=1} (i+1) \]
***Step 2*** From the outcome of step 1, subtract the following
\[ \sum^{i=50}_{i=1} (i+1) \]




<h5>Step 1</h5> Evaluate the following expression using the identities. In this step $n=100$
\[ \sum^{i=100}_{i=1} (i+1)  = \sum^{i=100}_{i=1} i  +  \sum^{i=100}_{i=1} 1  \]

1. First term \[\sum^{i=100}_{i=1} i  = \frac{100\times(100+1)}{2}  = 5050\]
2. Second term \[ \sum^{i=100}_{i=1} i  =  100\]


\[ \sum^{i=100}_{i=1} (i+1)  = 5050 + 100 = 5150 \]




<h5>Step 2</h5>
Evaluate the following expression using the identities. In this step $n=50$
\[ \sum^{i=50}_{i=1} (i+1)  = \sum^{i=50}_{i=1} i  +  \sum^{i=50}_{i=1} 1  \]

1. First term \[\sum^{i=50}_{i=1} i  = \frac{50\times(50+1)}{2}  = 1275\]
2. Second term \[ \sum^{i=50}_{i=1} i  =  50\]


\[ \sum^{i=50}_{i=1} (i+1)  = 1275 + 50 = 1325 \]


\[ \sum^{i=100}_{i=51} (i+1) = \sum^{i=100}_{i=1} (i+1)  - \sum^{i=50}_{i=1}(i+1)   \]

\[ \sum^{i=100}_{i=51} (i+1)  = 5150 - 1325 =\boldsymbol{3825} \]

### Sequences and Series


### Telescoping Series

#### Telescoping Series

* Telescoping Series - Worked Example - <a href="http://Telescoping%20Series (Lecture)" >HERE</a>[6:20]

* Telescoping Series - Worked Example - <a href="http://Telescoping%20Series (Lecture)" >HERE</a>[6:20]



*  <a href="https://www.youtube.com/watch?v=CcYnFbo8-xw">Telescoping Series (Lecture)</a>
*  Telescoping Series - Worked Example - <a href="http://Telescoping%20Series (Lecture)" >HERE</a>



*  <a href="https://www.youtube.com/watch?v=CcYnFbo8-xw">Telescoping Series (Lecture)</a>
*  Telescoping Series - Worked Example - <a href="http://Telescoping%20Series (Lecture)" >HERE</a>


*  Telescoping Series - Worked Example - <a href="http://Telescoping%20Series (Lecture)" >HERE</a>[6:20]




Proof By Induction {data-navmenu="Section 5"}
=====================================

Column
----------------------------------

### Proof by Induction

* <a href="https://www.youtube.com/watch?v=Jqd_Mvpxsbo">Proof By Induction </a>/
* <a href="https://www.youtube.com/watch?v=Jqd_Mvpxsbo">Proof By Induction </a>
* <a href="https://www.youtube.com/watch?v=1q21_hbmZG8">Proof By Induction </a>
	

		
#### Revision Notes
  
*  <a href="https://www.youtube.com/watch?v=VbO3eX1YKiM">Proof By Induction Example </a>
	
#### Series 

*  Evaluating the Sum of a Series – <a href="http://youtu.be/NhUBAYcfY_A" >HERE</a> 
#### Convergence Testing 

*  <a  href="https://www.youtube.com/watch?v=1owq4xezLng">Convergence Test</a>
*  Ratio Test Exercise – <a href="http://youtu.be/ojL-Vtek2Mo" >HERE</a> [5:19]






Probability {data-navmenu="Section 6"}
=====================================

Column {.tabset}
-------------------------------------------------

### Basics of Probability


### Room 1

<h5> High-Level APIs for Machine Learning (Iain Keaney) </h5>

Convergence Testing {data-navmenu="Section 5"}
=========================================

### Convergence Tests


*  <a href="https://www.youtube.com/watch?v=1owq4xezLng">Convergence Test</a>
*  Ratio Test Exercise – <a href="http://youtu.be/ojL-Vtek2Mo" >HERE</a> [5:19]

*  Convergence Test- <a href="https://youtu.be/LWYiiY1rOqg" >HERE</a>(3:13)
*  Ratio Test Exercise – <a href="https://youtu.be/Ka8OawOt_-w" >HERE</a>[5:19]


#### Ratio Test


*  Ratio Test (2015 Exam Question) - <a href="https://youtu.be/TApQUje2kWs" >HERE</a>
*  Ratio Test for Convergence (2011 Q4) - <a href="https://youtu.be/u5grewDLe68" >HERE</a>


#### Ratio Test

*  Ratio Test (2009 Exam Question) - <a href="https://youtu.be/0sjwarDSa-0" >HERE</a>
*  Important Taylor Series Expansions <a href="https://youtu.be/ItK4oTbuuOo" >HERE</a>
*  Maclaurin Series Worked Example  <a href="https://youtu.be/tc-Zelm9bWA" >HERE</a>
*  <a href="https://www.youtube.com/watch?v=Ka8OawOt_-w">Simple Ratio Test Exercise	 </a>
  
*  <a href="https://www.youtube.com/watch?v=quK-JQ5EQOE">The Ratio Test</a>
	
#### Ratio Test

*  Convergence Test- <a href="https://youtu.be/LWYiiY1rOqg" >HERE</a>(3:13)
*  Ratio Test Exercise – <a href="https://youtu.be/Ka8OawOt_-w" >HERE</a>[5:19]
*  Ratio Test (2015 Exam Question) - <a href="https://youtu.be/TApQUje2kWs" >HERE</a>
*  Ratio Test for Convergence (2011 Q4) - <a href="https://youtu.be/u5grewDLe68" >HERE</a>
*  Ratio Test (2009 Exam Question) - <a href="https://youtu.be/0sjwarDSa-0" >HERE</a>


#### Convergence Testing 

*  <a  href="https://www.youtube.com/watch?v=1owq4xezLng">Convergence Test</a>
*  Ratio Test Exercise – <a href="http://youtu.be/ojL-Vtek2Mo" >HERE</a> [5:19]





 
  
*  <a href="https://www.youtube.com/watch?v=ItK4oTbuuOo">Important Taylor Series Expansions  </a>
	 
*  <a href="https://www.youtube.com/watch?v=tc-Zelm9bWA">Maclaurin Series Worked Example</a>
	

#### Convergence Testing 

*  <a  href="https://www.youtube.com/watch?v=1owq4xezLng">Convergence Test</a>
*  Ratio Test Exercise – <a href="http://youtu.be/ojL-Vtek2Mo" >HERE</a> [5:19]



   


```{r child="sourcefiles/Matrices-IntroductionToMatrices.Rmd"}
```



Counting Problems {data-navmenu="Section 6"}
==================================

Column {.tabset}
-----------------------------

### Counting Problems

<h5> Counting Problems </h5>


In this section we look at counting problems, including combinations and permutations.


#### Videos


* Counting Problems -  <a href="https://www.youtube.com/watch?v=9QVx6yXzfEM" >HERE</a>
* Binomial Coefficients - <a href="https://youtu.be/S74rTbwKIDY" >HERE</a>
* Probability and Combinations (The Hypergeometric Distribution) - <a href="https://www.youtube.com/edit?o=U&amp;video_id=BdkSlLgd5dc" >HERE</a>(12:49)


  
* <a href ="https://www.youtube.com/watch?v=/O2Xg1BdqQBM"> Binomial Coefficients - Proof of Identities 1</a>
* <a href ="https://www.youtube.com/watch?v=/XXoUYJbESCY"> Binomial Coefficients - Proof of Identities 2</a>
* <a href ="https://www.youtube.com/watch?v=/O8P0te8s-ms"> Binomial Coefficients - Examples</a> /
* <a href ="https://www.youtube.com/watch?v=/ytvlX_-VrF8"> Binomial Coefficients - Proof of Identities 3</a> 
* <a href ="https://www.youtube.com/watch?v=/ong5YXLf_7Q"> Binomial Coefficients - Team Selection</a>
* <a href ="https://www.youtube.com/watch?v=/oWlmy3W92u4"> Permutations and Combinations</a>

### Combinations

<h5> Combinations </h5>

### Permutations
