---
title: "Discrete Mathematics - Section 9"
output: 
  flexdashboard::flex_dashboard:
    theme: united
    css: style.css
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

```



Trees {data-navmenu="Trees"}
=====================================

Column {.tabset}
-------------------------------------------------

### Trees 
<a href="index.html">Back to main page</a>


<h3>Section 9: Trees</h3>

In graph theory, a tree is an undirected graph in which any two vertices are connected by exactly one path, or equivalently a connected acyclic undirected graph.


Spanning Trees {data-navmenu="Spanning Trees"}
=====================================

Column {.tabset}
-------------------------------------------------


### Spanning Trees

#### Spanning Trees
Let G be a connected graph, then the sub-graph H of G is called a spanning tree of G if −

* H is a tree
* H contains all vertices of G.
A spanning tree T of an undirected graph G is a subgraph that includes all of the vertices of G.

### Kirchoff’s Theorem
Kirchoff’s theorem is useful in finding the number of spanning trees that can be formed from a connected graph.

#### Example

Kirchoff’s Theorem
The matrix ‘A’ be filled as, if there is an edge between two vertices, then it should be given as ‘1’, else ‘0’.

A=∣∣∣∣∣∣∣0abcda0111b1001c1001d1110∣∣∣∣∣∣∣=∣∣∣∣∣∣0111100110011110∣∣∣∣∣∣
By using kirchoff's theorem, it should be changed as replacing the principle diagonal values with the degree of vertices and all other elements with -1.A

=∣∣∣∣∣∣3−1−1−1−120−1−102−1−1−1−13∣∣∣∣∣∣=M
M=∣∣∣∣∣∣3−1−1−1−120−1−102−1−1−1−13∣∣∣∣∣∣=8
Cofactorofm1=∣∣∣∣20−102−1−1−13∣∣∣∣

Thus, the number of spanning trees = 8.

```{r child="Section_09/Graphs-Trees.Rmd"}
```


```{r child="sourcefiles/Graphs-BinarySearchTrees.Rmd"}
```

```{r child="Section_09/BinarySearchTrees.Rmd"}
```


```{r child="TutorialSheets/Trees-Tutorial-1.Rmd"}
```

