---
title: "Discrete Mathematics - Section 11"
output: 
  flexdashboard::flex_dashboard:
    theme: united
    css: style.css
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

```


Discrete Mathematics {data-navmenu="Introduction"}
=====================================

Column {.tabset}
--------------------

### Sequences and Series

<a href="index.html">Back to main page</a>


<h3>Section 11</h3>

In mathematics, the sequence is a collection or list of numbers that have a logical/sequential order or pattern between them. 
<p>
For example, 1, 5, 9, 13, … is a sequence having a difference of 4 between each consecutive next term and each term can be represented in form 1 + 4 * ( n – 1 ) where n is the nth term of the sequence. 
<p>
The sequence can be classified into 3 categories:

1. Arithmetic Sequence
2. Geometric Sequence
3. Harmonic Sequence




----------------------------------------------------------------------------------
### {Aritmetic Progressions}

An arithmetic progression (AP) or arithmetic sequence is a sequence of numbers such that the difference between the consecutive terms is constant. 
For instance, the sequence $5, 7, 9, 11, 13, 15 \ldots$ is an arithmetic progression with common difference of 2.

----------------------------------------------------------------------------------


If the initial term of an arithmetic progression is $a_{1}$ and the common difference of successive members is d, then the $n-$th term of the sequence ($a_{n}$) is given by:
\[ a_{n}=a_{1}+(n-1)d, \] 
and in general
\[ a_{n}=a_{m}+(n-m)d.\]


----------------------------------------------------------------------------------

A finite portion of an arithmetic progression is called a \textbf{finite arithmetic progression} and sometimes just called an arithmetic progression. The sum of a finite arithmetic progression is called an arithmetic series.


----------------------------------------------------------------------------------


The behavior of the arithmetic progression depends on the common difference d. If the common difference is:

* Positive, the members (terms) will grow towards positive infinity.
* Negative, the members (terms) will grow towards negative infinity.




---------------------------------------------------------------------------------
\textbf{Summation of an Arithmetic Progression}
The sum of the members of a finite arithmetic progression is called an arithmetic series. For example, consider the sum:
\[2+5+8+11+14\]
This sum can be found quickly by taking the number n of terms being added (here 5), multiplying by the sum of the first and last number in the progression (here 2 + 14 = 16), and dividing by 2:
\[{\frac  {n(a_{1}+a_{n})}{2}}\]


In the case above, this gives:
\[2+5+8+11+14={\frac  {5(2+14)}{2}}={\frac  {5\times 16}{2}}=40.\]
This formula works for any real numbers $a_{1}$ and $a_{n}$. For example:
\[\left(-{\frac  {3}{2}}\right)+\left(-{\frac  {1}{2}}\right)+{\frac  {1}{2}}={\frac  {3\left(-{\frac  {3}{2}}+{\frac  {1}{2}}\right)}{2}}=-{\frac  {3}{2}}.\]

----------------------------------------------------------------------------------

\textbf{Arithmetic Progressions}

------1.5cm}
Find the sum of the arithmetic progression
{

\[ 11 + 13 + 15 + \ldots + 49 + 51 \]
}


----------------------------------


\textbf{Arithmetic Progressions}

------0.5cm}
First recall two useful equations for working with arithmetic progressions.\\
\bigskip


For the arithmetic sequence $a,(a+d) ,(a+2d), \ldots$


[(i)] $t_n$ is the $n-th$ term of series.\[ t_n= a+(n-1)d \]

[(ii)] $S_n$ is the sum of the first $n$ terms

\[ S_n  = \frac{n }{ 2} \left[ 2a+(n-1)d \right] \]



----------------------------------


\textbf{Arithmetic Progressions}

Find the sum of the arithmetic progression
{
\[ 11 + 13 + 15 + \dots + 49 + 51 \]
}

* Note that $a=11$ and $d=2$.
* We need to find out what $n$ (the number of terms) is.
* The last term is $51$.



----------------------------------


\textbf{Arithmetic Progressions}



* The last term is $51$.
* $t_n$ = 51 = [ 11 + (n-1)2 ] 
* $t_n$ = 51 = 2n + 9
* $n=21$

There are 21 terms in the series.


----------------------------------


\textbf{Arithmetic Progressions}


\[ S_n  = {n \over 2} \left[ 2a+(n-1)d \right] \]

Recall $a=11$,$d=2$ and $n=21$


\[ \phantom{S_n  = {21 \over 2} \left[ (2.11) +[(21-1)2] \right]} \]
\[ \phantom{S_n  = 10.5 \left[ 22 + 40 \right]  = 10.5 \times 62}\]
\[ \phantom{S_n  = 651} \] 





```{r child="Section_11/SequenceSeries-Progressions.Rmd"}
```





```{r child="Section_11/SequenceSeries-IntroductionToSequencesSeries.Rmd"}
```



```{r child="Section_11/SequenceSeries-FiniteSeries.Rmd"}
```





```{r child="Section_11/SequenceSeries-RecurrenceRelations.Rmd"}
```


```{r child="Section_11/SequenceSeries-TelescopingSeries.Rmd"}
```



```{r child="TutorialSheets/Series-Tutorial-1.Rmd"}
```