---
title: "Discrete Mathematics - Section 3"
output: 
  flexdashboard::flex_dashboard:
    theme: united
    css: style.css
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

```


About {data-navmenu="About"}
=====================================

Column {.tabset}
--------------------

### Set Theory

<a href="index.html">Back to main page</a>


<h3>Set Theory</h3>

* Set theory is used throughout mathematics. It is used as a foundation for many sub-fields of mathematics. In the areas pertaining to statistics, it is particularly used in probability. 
* Much of the concepts in probability are derived from the consequences of set theory. 
* Indeed, one way to state the axioms of probability involves set theory.




### Subsets and Elements of Sets

<h3> Subsets and Elements of Sets </h3>

#### Elements of a Set

*  Sets are comprised of members, which are often called ***elements***. 
*  If a particular value ($k$) is an element of set $A$, then we would write this as
\[k \in A \]

*  If a single value $k$ is not an element of set $A$, then we write
\[k \notin A \]



#### Proper Subsets
Given two sets $A$ and $B$, the set $A$ is a ***proper subset*** of set $B$ if every element of $A$ is also an element of $B$, but there are elements of set $B$ that are not in set $A$.


We write this mathematically as
\[A \subset B \]


```{r child="Section_03/Set-IntroductionToSet.Rmd"}
```

```{r child="Section_03/Set-SpecifyingSets.Rmd"}
```






```{r child="Section_03/Set-SetOperations.Rmd"}
```

```{r child="Section_03/Set-MembershipTables.Rmd"}
```


```{r child="Section_03/Set-PowerSets.Rmd"}
```

```{r child="Section_03/Set-Theory-Tutorial-1.Rmd"}
```
```{r child="Section_03/Set-Theory-Tutorial-2.Rmd"}
```

