---
title: "Discrete Mathematics - Section 1"
output: 
  flexdashboard::flex_dashboard:
    theme: united
    css: style.css
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

```


Discrete Mathematics {data-navmenu="Introduction"}
=====================================

Column {.tabset}
--------------------


### Part 1. Number Bases

*  Numbers in Base 10
*  The binary system
*  Calculating in the binary system
*  The Hexadecimal system
*  Converting decimal integers into other bases


### Part 2. Rational Numbers

*  Factor, multiples and primes
*  Representing fractions
*  Decimal fractions
*  Fractions in bases other than 10


### Part 3. Real Numbers

*  Irrational numbers
*  Inequality symbols
*  Floating-point notation


* <a href="https://www.youtube.com/watch?v=/9NAmHx3pAxk" >Number Sets: Natural Numbers, Integers, Rational Numbers and Real Numbers.</a>
* <a href="https://www.youtube.com/watch?v=/lu7uhe903TY" >Irrational Numbers: Exercise involving irrational numbers.</a>
* <a href="https://www.youtube.com/watch?v=/WnXnVADCXuQ" >Rational and Irrational Numbers</a>

* <a href="https://www.youtube.com/watch?v=/mhHAJOQQ8kM" >Repeating Decimals</a>
* <a href="https://www.youtube.com/watch?v=/99qV28WmzH4" >Repeating Decimals</a>
* <a href="https://www.youtube.com/watch?v=/sIowD1XjFJ8" >Repeating Decimals</a>



```{r child="sourcefiles/Numbers-IntroductionToNumbers.Rmd"}
```


