---
title: "Discrete Mathematics - Section 5"
output: 
  flexdashboard::flex_dashboard:
    theme: united
    css: style.css
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

```


Discrete Mathematics {data-navmenu="Introduction"}
=====================================

Column {.tabset}
--------------------

### Functions 

<a href="index.html">Back to main page</a>

<h3>Section 5: Functions (Part 1)</h3>



* Introduction to Functions
* Mathematical Functions and Special Functions

### Laws of Logarithms


### Laws of Logarithms



Here we
assume x and y are positive real numbers.
1. $loga(xy) = loga(x) + loga(y)$
2. $loga(x/y)= loga(x) - loga(y)$
3. $loga (x^r) = r loga(x)$ for any real number r.




Here we
assume x and y are positive real numbers.


1. $\log_a(xy) = loga(x) + \log_a(y)$

2. $loga(x/y)= loga(x) - loga(y)$

3. $\log_a (x^r) = r \log_a(x)$ for any real number r.




 
```{r child="Section_05/Functions-MathsFunctions.Rmd"}
```

```{r child="Section_05/Functions-MathsFunctions.Rmd"}
```

```{r child="TutorialSheets/Functions-Tutorial-1.Rmd"}
```

