---
title: "Discrete Mathematics - Section 3"
output: 
  flexdashboard::flex_dashboard:
    theme: united
    css: style.css
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

```


About {data-navmenu="About"}
=====================================

Column {.tabset}
--------------------

### Set Theory

<a href="index.html">Back to main page</a>


<h3>Set Theory</h3>

* Set theory is used throughout mathematics. It is used as a foundation for many sub-fields of mathematics. In the areas pertaining to statistics, it is particularly used in probability. 
* Much of the concepts in probability are derived from the consequences of set theory. 
* Indeed, one way to state the axioms of probability involves set theory.



### Set Notation


**Set Notation**

In mathematics, a set is a well-defined collection of distinct objects. These objects, which can be anything from numbers and letters to more complex entities, are called the **elements** of the set.

**How to Represent Sets**

There are two primary ways to represent sets:

1. **Roster Notation:**
   - Enclose the elements of the set within curly braces `{}`.
   - Separate the elements with commas.

   **Example:**
   * The set of the first three natural numbers: `{1, 2, 3}`
   * The set of vowels in the English alphabet: `{a, e, i, o, u}`

2. **Set-Builder Notation:**
   - Define a set by specifying a property that its elements must satisfy.
   - The general form is: `{x | condition(x)}`, which reads "the set of all x such that x satisfies condition(x)".

   **Example:**
   * The set of even numbers: `{x | x is an integer and x is divisible by 2}`
   * The set of prime numbers: `{p | p is an integer greater than 1 and has no divisors other than 1 and itself}`

**Common Set Symbols**

* **∈:** "is an element of" (e.g., `x ∈ A` means "x is an element of set A")
* **∉:** "is not an element of"
* **⊆:** "is a subset of" (e.g., `A ⊆ B` means "set A is a subset of set B", meaning all elements of A are also in B)
* **⊂:** "is a proper subset of" (means A is a subset of B, but A is not equal to B)
* **∪:** "union" (represents the set of elements that are in either set A or set B)
* **∩:** "intersection" (represents the set of elements that are in both set A and set B)
* **-:** "set difference" (represents the set of elements that are in A but not in B)
* **∅** or {}: "empty set" (the set containing no elements)
* **U:** "universal set" (the set containing all possible elements in a given context)

**Examples**

* **Set A = {1, 2, 3, 4, 5}`**
* **Set B = {3, 4, 5, 6, 7}`**

* **A ∪ B = {1, 2, 3, 4, 5, 6, 7}`**
* **A ∩ B = {3, 4, 5}`**
* **A - B = {1, 2}`**
* **B - A = {6, 7}`**

**Visualizing Sets: Venn Diagrams**

Venn diagrams are a useful tool for visualizing relationships between sets. They use overlapping circles to represent sets and their intersections.

**Key Points**

* Sets are fundamental in mathematics and computer science.
* Understanding set notation is crucial for expressing and manipulating sets effectively.
* Venn diagrams provide a visual aid for understanding set operations.
* Set theory has numerous applications in various fields, including database systems, artificial intelligence, and graph theory.



### Subsets and Elements of Sets

<h3> Subsets and Elements of Sets </h3>

#### Elements of a Set

*  Sets are comprised of members, which are often called ***elements***. 
*  If a particular value ($k$) is an element of set $A$, then we would write this as
\[k \in A \]

*  If a single value $k$ is not an element of set $A$, then we write
\[k \notin A \]



#### Proper Subsets
Given two sets $A$ and $B$, the set $A$ is a ***proper subset*** of set $B$ if every element of $A$ is also an element of $B$, but there are elements of set $B$ that are not in set $A$.


We write this mathematically as
\[A \subset B \]


```{r child="Section_03/Set-IntroductionToSet.Rmd"}
```

```{r child="Section_03/Set-SpecifyingSets.Rmd"}
```






```{r child="Section_03/Set-SetOperations.Rmd"}
```

```{r child="Section_03/Set-MembershipTables.Rmd"}
```

```{r child="Section_03/Set-TypesOfSet.Rmd"}
```

```{r child="Section_03/Set-PowerSets.Rmd"}
```

```{r child="Section_03/Set-De-Morgans-Laws.Rmd"}
```

```{r child="Section_03/Set-Theory-Tutorial-1.Rmd"}
```
```{r child="Section_03/Set-Theory-Tutorial-2.Rmd"}
```

