---
title: "Discrete Mathematics - Section 11"
output: 
  flexdashboard::flex_dashboard:
    theme: united
    css: style.css
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

```


Discrete Mathematics {data-navmenu="Introduction"}
=====================================

Column {.tabset}
--------------------

### Sequences and Series

<a href="index.html">Back to main page</a>


<h3>Section 11</h3>

In mathematics, the sequence is a collection or list of numbers that have a logical/sequential order or pattern between them. 
<p>
For example, 1, 5, 9, 13, … is a sequence having a difference of 4 between each consecutive next term and each term can be represented in form 1 + 4 * ( n – 1 ) where n is the nth term of the sequence. 
<p>
The sequence can be classified into 3 categories:

1. Arithmetic Sequence
2. Geometric Sequence
3. Harmonic Sequence

```{r child="Section_11/SequenceSeries-Progressions.Rmd"}
```





```{r child="Section_11/SequenceSeries-IntroductionToSequencesSeries.Rmd"}
```



```{r child="Section_11/SequenceSeries-FiniteSeries.Rmd"}
```





```{r child="Section_11/SequenceSeries-RecurrenceRelations.Rmd"}
```


```{r child="Section_11/SequenceSeries-TelescopingSeries.Rmd"}
```



```{r child="TutorialSheets/Series-Tutorial-1.Rmd"}
```