---
title: "Discrete Mathematics - Section 5"
output: 
  flexdashboard::flex_dashboard:
    theme: united
    css: style.css
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

```


Discrete Mathematics {data-navmenu="Introduction"}
=====================================

Column {.tabset}
--------------------

### Functions 

<a href="index.html">Back to main page</a>

<h3>Section 5: Functions (Part 1)</h3>



* Introduction to Functions
* Mathematical Functions and Special Functions

### Laws of Logarithms


#### Laws of Logarithms



Here we
assume x and y are positive real numbers.
1. $loga(xy) = loga(x) + loga(y)$
2. $loga(x/y)= loga(x) - loga(y)$
3. $loga (x^r) = r loga(x)$ for any real number r.




Here we
assume x and y are positive real numbers.


1. $\log_a(xy) = loga(x) + \log_a(y)$

2. $loga(x/y)= loga(x) - loga(y)$

3. $\log_a (x^r) = r \log_a(x)$ for any real number r.



---------------------------------------------------------
#### {Powers}

\[  2^ 4 = 2 \times 2 \times 2 \times 2 = 16 \]

\[  5^ 3 = 5 \times 5 \times 5 =125 \]

#### Special Cases 

Anything to the power of zero is always 1

\[  X^ 0 = 1 \mbox{ for all values of X} \]

Sometimes the power is a negative number.

\[  X^{-Y} = { 1 \over X^Y}  \]

Example 
\[  2^{-3} = { 1 \over 2^3} = { 1 \over 8}  \]

---------------------------------------------------------
#### {Exponentials Functions}

\[ e^a \times e^b = e^{a+b}\]

\[ (e^a )^b = e^{ab}\]



---------------------------------------------------------
#### {Precision Functions}


* Absolute Value Function $| x |$
* Ceiling Function $\lceil x \rceil$
* Floor Function  $\lfloor x \rfloor $

%\[ \lfloorx\rfloor\]

 \textbf{Question1.2}: 
 
State the range and domain of the following function
\[ F(x) = \lfloor x-1 \rfloor \]


\subsubsection{Special Cases}

Anything to the power of zero is always 1

\[  X^ 0 = 1 \mbox{ for all values of X} \]




 
```{r child="Section_05/Functions-MathsFunctions.Rmd"}
```

```{r child="Section_05/Functions-MathsFunctions.Rmd"}
```

```{r child="TutorialSheets/Functions-Tutorial-1.Rmd"}
```

