---
title: "Discrete Mathematics - Section 7"
output: 
  flexdashboard::flex_dashboard:
    theme: united
    css: style.css
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

```

About {data-navmenu="About"}
=====================================

Column {.tabset}
--------------------

### Functions (Part 3)


<a href="index.html">Back to main page</a>

<h3>Functions - Part 3</h3>

This section comprises some key items related to the application of functions in computer science.

***Big O Notation*** (with a capital letter O, not a zero), also called Landau's symbol, is a symbolism used in complexity theory, computer science, and mathematics to describe the asymptotic behavior of functions. Basically, it tells you how fast a function grows or declines.



```{r child = "navigate.Rmd"}
```


### Big O Notation

***Big O Notation*** 

Big O notation is one of the most fundamental tools for computer scientists to analyze the cost of an algorithm. It is a good practice for software engineers to understand in-depth as well.

### Growth of Functions

```{r child="Section_06/Functions-O-Notation.Rmd"}
```


```{r child="Section_05/Functions-Logarithms.Rmd"}
```

