---
title: "Discrete Mathematics - Section 9"
output: 
  flexdashboard::flex_dashboard:
    theme: united
    css: style.css
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

```


About {data-navmenu="About"}
=====================================


Column {.tabset}
-------------------------------------------------

### Trees 
<a href="index.html">Back to main page</a>


<h3>Trees</h3>

In graph theory, a tree is an undirected graph in which any two vertices are connected by exactly one path, or equivalently a connected acyclic undirected graph.


```{r child = "navigate.Rmd"}
```



Spanning Trees {data-navmenu="Spanning Trees"}
=====================================

Column {.tabset}
-------------------------------------------------


### Spanning Trees

<h3>Spanning Trees</h3>
A spanning tree of a graph is a subgraph that includes all the vertices of the original graph and is a tree. 
Recall: A tree is a connected, acyclic graph. Therefore, a spanning tree connects all the vertices together with the minimum number of edges required to maintain connectivity and without forming any cycles.

#### Definition

Let G be a connected graph, then the sub-graph H of G is called a spanning tree of G if −

* H is a tree
* H contains all vertices of G.
A spanning tree T of an undirected graph G is a subgraph that includes all of the vertices of G.

#### Key Points About Spanning Trees:
- **Includes All Vertices**: A spanning tree must include all vertices from the original graph.
- **Minimum Edges**: For a graph with \(n\) vertices, a spanning tree has exactly \(n-1\) edges.
- **No Cycles**: Spanning trees do not contain any cycles, ensuring the structure remains a tree.
- **Connectivity**: Despite having the minimum number of edges, a spanning tree maintains the graph's connectivity.

#### Examples:
Consider a simple graph:
```
A - B - C
|   |
D - E
```

Possible spanning trees of this graph include:
1. 
```
A - B - C
|   
D - E
```

2. 
```
A - B
|   
D - E - C
```

#### Applications:
- **Network Design**: Ensuring all nodes in a network are connected with the minimum number of connections.
- **Optimization**: Used in algorithms to minimize the cost of connecting points.
- **Cluster Analysis**: In data clustering algorithms to find minimal connecting clusters.

#### Algorithms to Find Spanning Trees:
- **Kruskal's Algorithm**: Finds the minimum spanning tree by adding the smallest edges while avoiding cycles.
- **Prim's Algorithm**: Builds the minimum spanning tree by starting from an arbitrary vertex and adding the smallest edge that expands the tree.

Spanning trees play a crucial role in network design, optimization problems, and various applications in computer science and mathematics.



### Kirchoff’s Theorem

**Kirchhoff’s Theorem**, also known as the Matrix-Tree Theorem, is a fundamental result in graph theory. It relates the number of spanning trees of a connected graph to the determinant of a specific matrix derived from the graph. This theorem is named after Gustav Kirchhoff, a physicist who made significant contributions to the understanding of electrical circuits and graph theory.

#### Theorem Statement:
Let \( G \) be a connected graph with \( n \) vertices. Construct the Laplacian matrix \( L \) of \( G \), which is defined as:
\[ L = D - A \]
where:
- \( D \) is the degree matrix: a diagonal matrix where the \( i \)-th diagonal element is the degree of the \( i \)-th vertex.
- \( A \) is the adjacency matrix: a matrix where the element \( A_{ij} \) is 1 if there is an edge between vertex \( i \) and vertex \( j \), and 0 otherwise.

#### Kirchhoff’s Theorem:
The number of spanning trees \( \tau(G) \) of a graph \( G \) is equal to any cofactor of the Laplacian matrix \( L \). More formally:
\[ \tau(G) = \det(L_{ij}) \]
where \( L_{ij} \) is the matrix obtained by deleting the \( i \)-th row and \( j \)-th column from \( L \).

#### Example:
Consider a simple graph \( G \) with vertices \( A, B, C \) and edges \( \{(A,B), (A,C), (B,C)\} \).

1. **Degree Matrix \( D \)**:
   \[
   D = \begin{pmatrix}
   2 & 0 & 0 \\
   0 & 2 & 0 \\
   0 & 0 & 2 \\
   \end{pmatrix}
   \]

2. **Adjacency Matrix \( A \)**:
   \[
   A = \begin{pmatrix}
   0 & 1 & 1 \\
   1 & 0 & 1 \\
   1 & 1 & 0 \\
   \end{pmatrix}
   \]

3. **Laplacian Matrix \( L \)**:
   \[
   L = D - A = \begin{pmatrix}
   2 & -1 & -1 \\
   -1 & 2 & -1 \\
   -1 & -1 & 2 \\
   \end{pmatrix}
   \]

4. **Deleting the First Row and Column of \( L \)**:
   \[
   L_{11} = \begin{pmatrix}
   2 & -1 \\
   -1 & 2 \\
   \end{pmatrix}
   \]

5. **Determinant of \( L_{11} \)**:
   \[
   \det(L_{11}) = (2 \times 2) - (-1 \times -1) = 4 - 1 = 3
   \]

Thus, the number of spanning trees \( \tau(G) \) in the given graph \( G \) is 3.

#### Example

Kirchhoff’s Theorem is a powerful tool in combinatorial mathematics and has applications in network reliability, electrical engineering, and more. Let me know if you need further clarification or examples!**Kirchhoff’s Theorem**, also known as the Matrix-Tree Theorem, is a fundamental result in graph theory. It relates the number of spanning trees of a connected graph to the determinant of a specific matrix derived from the graph. This theorem is named after Gustav Kirchhoff, a physicist who made significant contributions to the understanding of electrical circuits and graph theory.

#### Theorem Statement:
Let \( G \) be a connected graph with \( n \) vertices. Construct the Laplacian matrix \( L \) of \( G \), which is defined as:
\[ L = D - A \]
where:
- \( D \) is the degree matrix: a diagonal matrix where the \( i \)-th diagonal element is the degree of the \( i \)-th vertex.
- \( A \) is the adjacency matrix: a matrix where the element \( A_{ij} \) is 1 if there is an edge between vertex \( i \) and vertex \( j \), and 0 otherwise.

#### Kirchhoff’s Theorem:
The number of spanning trees \( \tau(G) \) of a graph \( G \) is equal to any cofactor of the Laplacian matrix \( L \). More formally:
\[ \tau(G) = \det(L_{ij}) \]
where \( L_{ij} \) is the matrix obtained by deleting the \( i \)-th row and \( j \)-th column from \( L \).

#### Example:
Consider a simple graph \( G \) with vertices \( A, B, C \) and edges \( \{(A,B), (A,C), (B,C)\} \).

1. **Degree Matrix \( D \)**:
   \[
   D = \begin{pmatrix}
   2 & 0 & 0 \\
   0 & 2 & 0 \\
   0 & 0 & 2 \\
   \end{pmatrix}
   \]

2. **Adjacency Matrix \( A \)**:
   \[
   A = \begin{pmatrix}
   0 & 1 & 1 \\
   1 & 0 & 1 \\
   1 & 1 & 0 \\
   \end{pmatrix}
   \]

3. **Laplacian Matrix \( L \)**:
   \[
   L = D - A = \begin{pmatrix}
   2 & -1 & -1 \\
   -1 & 2 & -1 \\
   -1 & -1 & 2 \\
   \end{pmatrix}
   \]

4. **Deleting the First Row and Column of \( L \)**:
   \[
   L_{11} = \begin{pmatrix}
   2 & -1 \\
   -1 & 2 \\
   \end{pmatrix}
   \]

5. **Determinant of \( L_{11} \)**:
   \[
   \det(L_{11}) = (2 \times 2) - (-1 \times -1) = 4 - 1 = 3
   \]

Thus, the number of spanning trees \( \tau(G) \) in the given graph \( G \) is 3.

Kirchhoff’s Theorem is a powerful tool in combinatorial mathematics and has applications in network reliability, electrical engineering, and more. 

#### Example

### Kirchhoff’s Theorem

To understand Kirchhoff’s Theorem, we start with the adjacency matrix \( A \) of a graph. This matrix is filled such that if there is an edge between two vertices, the corresponding entry is '1'; otherwise, it is '0'.

For example, consider the following graph representation:

\[ 
A = 
\begin{pmatrix}
0 & 1 & 1 & 1 \\
1 & 0 & 0 & 1 \\
1 & 0 & 0 & 1 \\
1 & 1 & 1 & 0
\end{pmatrix}
\]

Using Kirchhoff’s Theorem, we transform the adjacency matrix \( A \) into the Laplacian matrix \( L \) by replacing the principal diagonal values with the degree of the respective vertices and setting all other elements to \(-1\):

\[ 
L = 
\begin{pmatrix}
3 & -1 & -1 & -1 \\
-1 & 2 & 0 & -1 \\
-1 & 0 & 2 & -1 \\
-1 & -1 & -1 & 3
\end{pmatrix}
\]

To determine the number of spanning trees, we need to find any cofactor of the Laplacian matrix \( L \). In this example, let's consider the cofactor obtained by removing the first row and first column:

\[ 
L_{11} = 
\begin{pmatrix}
2 & 0 & -1 \\
0 & 2 & -1 \\
-1 & -1 & 3
\end{pmatrix}
\]

Calculating the determinant of this submatrix:

\[ 
\det(L_{11}) = (2 \times 2 \times 3) - (2 \times (-1) \times (-1)) = 12 - 2 = 10 
\]

Thus, the number of spanning trees for the given graph is 10.

This rephrasing maintains the same mathematical steps while clarifying the process of applying Kirchhoff’s Theorem to determine the number of spanning trees in a graph. 

```{r child="Section_09/Graphs-Trees.Rmd"}
```


```{r child="sourcefiles/Graphs-BinarySearchTrees.Rmd"}
```

```{r child="Section_09/BinarySearchTrees.Rmd"}
```


```{r child="TutorialSheets/Trees-Tutorial-1.Rmd"}
```



Tutorial Videos {data-navmenu="Tutorial Videos"}
=====================================

Column {.tabset}
--------------------

### Tutorial Videos