---
title: "Discrete Mathematics - Section 1"
output: 
  flexdashboard::flex_dashboard:
    theme: united
    css: style.css
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

```


About {data-navmenu="About"}
=====================================

Column {.tabset}
--------------------

### Real Numbers

<a href="index.html">Back to main page</a>


<h4> Real Numbers</h4>

```{r eval=FALSE, echo=FALSE}
#<! -- https://www.cuemath.com/numbers/real-numbers/ -->
```

#### Real Numbers
Any number that can be found in the real world is a real number. We find numbers everywhere around us. Natural numbers are used for counting objects, rational numbers are used for representing fractions, irrational numbers are used for calculating the square root of a number, integers for measuring temperature, and so on. 

<p>
These different types of numbers make a collection of real numbers. In this lesson, we will learn all about real numbers and their important properties.

#### What are Real Numbers?

Any number that we can think of, except complex numbers, is a real number. The set of real numbers, which is denoted by R, is the union of the set of rational numbers (Q) and the set of irrational numbers (Q). So, we can write the set of real numbers as, R = Q ∪ Q. This indicates that real numbers include natural numbers, whole numbers, integers, rational numbers, and irrational numbers. 

For example, 3, 0, 1.5, 3/2, √5, and so on are real numbers.


#### Types of Real Numbers
We know that real numbers include rational numbers and irrational numbers. Thus, there does not exist any real number that is neither rational nor irrational. It simply means that if we pick up any number from R, it is either rational or irrational.

#### Rational Numbers

Any number which can be defined in the form of a fraction p/q is called a rational number. The numerator in the fraction is represented as 'p' and the denominator as 'q', where 'q' is not equal to zero. A rational number can be a natural number, a whole number, a decimal, or an integer. For example, 1/2, -2/3, 0.5, 0.333 are rational numbers.

#### Irrational Numbers

Irrational numbers are the set of real numbers that cannot be expressed in the form of a fraction p/q where 'p' and 'q' are integers and the denominator 'q' is not equal to zero (q≠0.). For example, π (pi) is an irrational number. π = 3.14159265...In this case, the decimal value never ends at any point. Therefore, numbers like √2, -√7, and so on are irrational numbers.

#### Symbol of Real Numbers
Real numbers are represented by the symbol R. Here is a list of the symbols of the other types of numbers.

N - Natural numbers
W - Whole numbers
Z - Integers
Q - Rational numbers
¯¯¯¯
Q
 - Irrational numbers

#### Subsets of Real Numbers
All numbers except complex numbers are real numbers. Therefore, real numbers have the following five subsets:

* Natural numbers: All positive counting numbers make the set of natural numbers, $N = {1, 2, 3, ...}$
* Whole numbers: The set of natural numbers along with 0 represents the set of whole numbers. W = {0, 1, 2, 3, ..}
* Integers: All positive counting numbers, negative numbers, and zero make up the set of integers. Z = {..., -3, -2, -1, 0, 1, 2, 3, ...}
* Rational numbers: Numbers that can be written in the form of a fraction p/q, where 'p' and 'q' are integers and 'q' is not equal to zero are rational numbers. Q = {-3, 0, -6, 5/6, 3.23}
* Irrational numbers: The numbers that are square roots of positive rational numbers, cube roots of rational numbers, etc., such as √2, come under the set of irrational numbers. ( 
¯

### Part 1. Number Bases

*  Numbers in Base 10
*  The binary system
*  Calculating in the binary system
*  The Hexadecimal system
*  Converting decimal integers into other bases


### Part 2. Rational Numbers

*  Factor, multiples and primes
*  Representing fractions
*  Decimal fractions
*  Fractions in bases other than 10




### Number Sets

<h4> Number Sets (Notation)
The font that the symbols are written in (i.e. $\mathbb{N}$, $\mathbb{R}$) is known as ***blackboard font***.

*  $\mathbb{N}$ Natural Numbers ($0,1,2,3$) 
(Not used in the CIS102 Syllabus)
*  $\mathbb{Z}$ Integers ($-3,-2,-1,0,1,2,3, \ldots$)

* [$\ast$] $\mathbb{Z}^{+}$ Positive Integers
* [$\ast$] $\mathbb{Z}^{-}$ Negative Integers

*  $\mathbb{Q}$ Rational Numbers
*  $\mathbb{R}$ Real Numbers

#### Sets of Numbers

*  $\mathbb{Z}$ Set of all integers
*  $\mathbb{Q}$ Set of all rational numbers
*  $\mathbb{R}$ Set of all real numbers


*  $\mathbb{Z}^{+}$ Set of all positive integers
*  $\mathbb{Z}^{-}$ Set of all negative integers
*  $\mathbb{R}^{+}$ Set of all positive real numbers
*  $\mathbb{R}^{-}$ Set of all negative real numbers


### Part 3. Real Numbers

*  Irrational numbers
*  Inequality symbols
*  Floating-point notation


* <a href="https://www.youtube.com/watch?v=/9NAmHx3pAxk" >Number Sets: Natural Numbers, Integers, Rational Numbers and Real Numbers.</a>
* <a href="https://www.youtube.com/watch?v=/lu7uhe903TY" >Irrational Numbers: Exercise involving irrational numbers.</a>
* <a href="https://www.youtube.com/watch?v=/WnXnVADCXuQ" >Rational and Irrational Numbers</a>

* <a href="https://www.youtube.com/watch?v=/mhHAJOQQ8kM" >Repeating Decimals</a>
* <a href="https://www.youtube.com/watch?v=/99qV28WmzH4" >Repeating Decimals</a>
* <a href="https://www.youtube.com/watch?v=/sIowD1XjFJ8" >Repeating Decimals</a>




<h4>Floating Point Numbers</h4>


* ***mantissa*** - the part of a floating-point number which represents the significant digits of that number.

* ***radix point*** - a radix point or radix character is a symbol used in the display of numbers to separate the integer part of the value from its fractional part. A decimal point is a well-known radix point.

### Cartestian Coordinates

* ***abscissa***



```{r child="Section_01/Introduction_To_Numbers.Rmd"}
```

```{r child  = "Section_01/Numbers-FractionalNumbers.Rmd"}
```


```{r child  = "Section_01/Floating_Point_Notation.Rmd"}
```




```{r child  = "Section_01/Scientific_Notation.Rmd"}
```

```{r child = "Section_01/Numbers-RepeatingDecimals.Rmd"}
```

