---
title: "Discrete Mathematics - Section 6"
output: 
  flexdashboard::flex_dashboard:
    theme: united
    css: style.css
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

```



About {data-navmenu="About"}
=====================================


Column {.tabset}
-------------------------------------------------

### Functions

<a href="index.html">Back to Main Page</a>


<h3>Functions</h3>

This section of the course, "Fundamentals of Functions in Mathematics," delves into the essential concepts and terminologies associated with functions. It provides a comprehensive understanding of the **domain**, **co-domain**, **image**, **ancestor**, and **range** of functions. Students will explore how functions are defined, represented, and analyzed, gaining insights into their fundamental properties. 

Through interactive activities, visual aids, and practical examples, this part of the course aims to equip students with the mathematical tools necessary to approach complex problems in computer science and related fields. By mastering these core concepts, students will be prepared for advanced studies and applications involving mathematical functions.



```{r child = "navigate.Rmd"}
```


Functions {data-navmenu="Function Fundamentals"}
=====================================

Column {.tabset}
-------------------------------------------------


### Functions


<h3>Functions</h3>

#### Objective:
By the end of this lesson, students will be able to define and differentiate between the concepts of Domain, Co-domain, Image, Ancestor, and Range in the context of mathematical functions.

#### Lesson Outline:

- **Domain**:
  - Definition: The set of all possible input values (independent variables) for which the function is defined.
  - Example: For \( f(x) = \sqrt{x} \), the domain is \( x \ge 0 \).

- **Co-domain**:
  - Definition: The set of all possible output values (dependent variables) that the function can produce.
  - Example: For \( f(x) = x^2 \), if the co-domain is all real numbers, then it includes both positive and negative values, even though the actual outputs (range) are non-negative.

- **Image**:
  - Definition: The actual output of the function for a specific input value.
  - Example: For \( f(x) = x + 2 \), the image of \( 3 \) is \( 5 \) (i.e., \( f(3) = 5 \)).

- **Ancestor**:
  - Definition: A value in the domain that maps to a specific value in the range.
  - Example: For \( f(x) = x^2 \), the ancestors of \( 9 \) in \( f(x) \) are \( 3 \) and \( -3 \).

- **Range**:
  - Definition: The set of all actual output values (images) that the function produces.
  - Example: For \( f(x) = x^2 \), the range is \( y \ge 0 \).


```{r child = "navigate.Rmd"}
```

### Polynomial Functions

#### Polynomial Functions


[Constants] $(P_0)$
[Linear Functions] $(P_1)$
[Quadratic Functions] $(P_2)$
[Cubic Functions] $(P_3)$

-----------------------------------

### Ordered Pairs

```{r echo=FALSE}
#https://math24.net/cartesian-product-sets.html
```

<h3>Ordered Pairs</h3>

In sets, the order of elements is not important. For example, the sets {2, 3} and {3, 2} are equal to each other. However, there are many instances in mathematics where the order of elements is essential. So, for example, the pairs of numbers with coordinates (2, 3) and (3, 2) represent different points on the plane. This leads to the concept of ordered pairs.

An ordered pair is defined as a set of two objects together with an order associated with them. Ordered pairs are usually written in parentheses (as opposed to curly braces, which are used for writing sets).

In the ordered pair  the element  is called the first entry or first component, and  is called the second entry or second component of the pair.

Two ordered pairs  and  are equal if and only if  and  In general,

The equality  is possible only if 

### Tuples
The concept of ordered pair can be extended to more than two elements. An ordered tuple is a set of  objects together with an order associated with them. Tuples are usually denoted by  The element   is called the  entry or component, and  is called the length of the tuple.

Similarly to ordered pairs, the order in which elements appear in a tuple is important. Two tuples of the same length  and  are said to be equal if and only if  for all  So the following tuples are not equal to each other:

Unlike sets, tuples may contain a certain element more than once:

Ordered pairs are sometimes referred as tuples.

### Cartesian Product of Two Sets
Suppose that  and  are non-empty sets. The Cartesian product of two sets  and  denoted  is the set of all possible ordered pairs  where  and 

The Cartesian product is also known as the cross product.

The figure below shows the Cartesian product of the sets  and 

Cartesian product of two sets A={1,2,3} and B={x,y}.
Figure 1.
It consists of  ordered pairs:

Similarly, we can find the Cartesian product 

As you can see from this example, the Cartesian products  and  do not contain exactly the same ordered pairs. So, in general, 

If  then  is called the Cartesian square of the set  and is denoted by 

#### Cartesian Product of Several Sets
Cartesian products may also be defined on more than two sets.

Let  be  non-empty sets. The Cartesian product  is defined as the set of all possible ordered tuples  where  and 

If  then  is called the  Cartesian power of the set  and is denoted by 

#### Properties

Some Properties of Cartesian Product
The Cartesian product is non-commutative:
 if only 
 if either  or 
The Cartesian product is non-associative:
Distributive property over set intersection:
Distributive property over set union:
Distributive property over set difference:
If  then  for any set 
Cardinality of Cartesian Product
The сardinality of a Cartesian product of two sets is equal to the product of the cardinalities of the sets:

Similarly,

See solved problems on Page 2.

### Videos
* <a href ="https://www.youtube.com/watch?v=/-3hd821alPI">Functions (2005 Q4 Part A)  </a>
* <a href ="https://www.youtube.com/watch?v=/cR5b2zWOa0w">Functions (2003 Q4 Part B) </a>
* <a href ="https://www.youtube.com/watch?v=/IXs5CTQnBU4">Floor Functions Exercise HD	</a>



### Cartesian Product

$X \times Y$

$X = \{1,2,3\}$

$Y = \{a,b,c\}$


$X \times Y = \{ (1,a) , (1,b) , (1,c) , (2,a), (2,b) ,(2,c), (3,a),(3,b),(3,c) \}$ 
$Y \times X = \{ (a,1) , (a,2) , (a,3) , (b,1), (b,2) ,(b,3), (c,1),(c,2),(c,3) \}$ 




Invertible Functions {data-navmenu="Invertible Functions"}
=====================================

Column {.tabset}
-------------------------------------------------

### Invertible Functions

Necessary Conditions for Invertibility of a Function

* The function must be one-to-one
* The fucntion must be onto.




* A function is ***onto*** if is range is equal to its codomain.

* A function is ***one-to-one*** if no two distinct elements of the domain have the same image.


Tutorial Videos {data-navmenu="Tutorials and Videos"}
=====================================

Column {.tabset}
--------------------

### Tutorial Videos