---
title: "Discrete Mathematics - Section 10"
output: 
  flexdashboard::flex_dashboard:
    theme: united
    css: style.css
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

```


Discrete Mathematics {data-navmenu="Introduction"}
=====================================

Column {.tabset}
--------------------

### Digraphs and Relations

<a href="index.html">Back to main page</a>


<h3>Digraphs and Relations</h3>


A directed graph, also called a digraph, is a graph in which the edges have a direction. 
This is usually indicated with an arrow on the edge; more formally, if $v$ and $w$ are vertices, an edge is an unordered pair ${v,w}$, while a directed edge, called an arc, is an ordered pair (v,w) or (w,v).

```{r child="sourcefiles/RelationsDigraphs-Introduction.Rmd"}
```


### Directed Graphs (Digraphs) in Graph Theory

#### Introduction to Digraphs
A directed graph, or digraph, is a type of graph where each edge has a direction associated with it, indicating a one-way relationship between two vertices. Digraphs are used to model various real-world systems, such as traffic networks, social media interactions, and web page links.

#### Basic Terminology
- **Vertex (Node)**: A fundamental unit or point in the graph.
- **Edge (Arc)**: A directed connection between two vertices. An edge from vertex \( u \) to vertex \( v \) is represented as \( (u, v) \).
- **In-degree**: The number of edges coming into a vertex.
- **Out-degree**: The number of edges going out from a vertex.
- **Adjacency List**: A list where each vertex stores the vertices to which it has outgoing edges.
- **Adjacency Matrix**: A matrix where the entry \( M[i][j] \) indicates the presence of a directed edge from vertex \( i \) to vertex \( j \).

#### Representing Digraphs
**1. Adjacency List Representation**
```
A -> B, C
B -> C
C -> A
D -> C
```
In this example, vertex \( A \) has outgoing edges to \( B \) and \( C \); vertex \( B \) has an outgoing edge to \( C \); and so on.

**2. Adjacency Matrix Representation**
```
    A B C D
A [ 0 1 1 0 ]
B [ 0 0 1 0 ]
C [ 1 0 0 0 ]
D [ 0 0 1 0 ]
```
Here, the matrix entry \( [A, B] \) is 1, indicating a directed edge from \( A \) to \( B \).

#### Traversal Algorithms for Digraphs
**1. Depth-First Search (DFS)**
DFS explores as far as possible along each branch before backtracking. It can be used to detect cycles and find paths in digraphs.

**DFS Algorithm**:
1. Start from a given vertex.
2. Mark the current vertex as visited.
3. Recursively visit all unvisited vertices adjacent to the current vertex.
4. Backtrack when no more adjacent unvisited vertices are found.

**Example**:
```
Input: A digraph with vertices {A, B, C, D}
Edges: (A, B), (A, C), (B, C), (C, A), (D, C)
Starting vertex: A
```
DFS Traversal: A -> B -> C

**2. Breadth-First Search (BFS)**
BFS explores all vertices at the present depth level before moving on to the vertices at the next depth level. It is useful for finding the shortest path in unweighted digraphs.

**BFS Algorithm**:
1. Start from a given vertex.
2. Mark the current vertex as visited and enqueue it.
3. Dequeue a vertex and explore all its adjacent unvisited vertices.
4. Enqueue each unvisited adjacent vertex and mark them as visited.
5. Repeat until the queue is empty.

**Example**:
```
Input: A digraph with vertices {A, B, C, D}
Edges: (A, B), (A, C), (B, C), (C, A), (D, C)
Starting vertex: A
```
BFS Traversal: A -> B -> C

#### Applications of Digraphs
- **Traffic Networks**: Modeling one-way streets and traffic flow.
- **Social Media**: Representing follower-followee relationships.
- **Web Page Links**: Analyzing link structures in search engines.
- **Task Scheduling**: Modeling dependencies between tasks.

#### Example Problems
**Example 1**: Detecting Cycles in a Digraph
- Use DFS to detect if there is a back edge (an edge that points to an ancestor) in the DFS tree.

**Example 2**: Finding Shortest Path in a Digraph
- Use BFS to find the shortest path in an unweighted digraph, or Dijkstra's algorithm for weighted digraphs.

#### Practice Exercises
1. Represent the following digraph using an adjacency list and adjacency matrix:
```
Vertices: {P, Q, R, S}
Edges: (P, Q), (P, R), (Q, R), (R, S), (S, P)
```
2. Perform a DFS traversal starting from vertex P.
3. Perform a BFS traversal starting from vertex P.
4. Detect cycles in the given digraph using DFS.

By mastering these concepts and techniques, you will have a solid understanding of directed graphs and their applications in various fields. 



Relations {data-navmenu="Relations"}
=====================================

Column {.tabset}
--------------------

### Relations

<h4>Types of Relations</h4>


#### Transitive Relations

Transitive relations are binary relations defined on a set such that if the first element is related to the second element, and the second element is related to the third element of the set, then the first element must be related to the third element. For example, if for three elements a, b, c in set A, if a = b and b = c, then a = c.


#### PArtial Order 

A partial order relation is a homogeneous relation that is transitive and antisymmetric. There are two common sub-definitions for a partial order relation, for reflexive and irreflexive partial order relations, also called "non-strict" and "strict" respectively.

```{r child="TutorialSheets/Digraphs-Tutorial-1.Rmd"}
```





### {Discrete Maths : Relations}

#### Example

* Let $A = \{2, 3, 4, 6\}$ and $B = \{4, 6, 9\}$
* Let R be the relation from A to B defined by \textit{\textbf{xRy}} if $x$
divides $y$ exactly.

