---
title: "Discrete Mathematics - Section 3"
output: 
  flexdashboard::flex_dashboard:
    theme: united
    css: style.css
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

```


Discrete Mathematics {data-navmenu="Introduction"}
=====================================

Column {.tabset}
--------------------

### Set Theory

<a href="index.html">Back to main page</a>


<h3>Set Theory</h3>

* Set theory is used throughout mathematics. It is used as a foundation for many sub-fields of mathematics. In the areas pertaining to statistics, it is particularly used in probability. 
* Much of the concepts in probability are derived from the consequences of set theory. 
* Indeed, one way to state the axioms of probability involves set theory.


### Specifying Sets


<h3>NOTATIONS FOR A SET:</h3>

A set can be represented by two methods:
1.ROSTER METHOD
2.BUILDER METHOD

#### ROSTER METHOD:

In this method the elements of a set are separated by commas and are enclosed within curly brackets { }. For example:

* A = {1, 2, 3, 4, 5, 6} is a set of numbers.

* $B = \{Albert, Brianna, Carmel, David, Edward\}$ is a set of names.

* $C = \{a, e, i, o, u\}$ is a set of vowels.

* D = {apple, banana, guava, orange, pear} is a set of fruits.

Listing the elements in this way is called Roster method. In this method, it is not necessary for the elements to be listed in a particular order. The elements of the set can be written just plainly, separated by commas and in any order.

<p> 
#### BUILDER METHOD:

This method is also called Property method. In Builder method, a set is represented by stating all the properties which are satisfied by the elements of that particular set only.

For example:

If A is a set of elements less than 0, then in Builder method it will be written as

A = {x: x < 0}, this statement is read as "the set of all x such that x is less than 0"

If A is a set of all real numbers less than 7, then in Builder method it is written as A = {x   R: x < 7}

Similarly,

* A = {2i: i is an integer} is a set of all even integers.

* $A = {x   R: x ? 2}$ is a set of all real numbers except 2.

* $A = \{x   R: x > 3 and x < 7\}$ is a set of real numbers greater than 3 but less than 7.

* A = {x   Z: x > 6} is a set of integers greater than 6.

* $A = {x   Z: 2x + 1}$ is a set of all odd integers.



### Subsets and Elements of Sets

<h3> Subsets and Elements of Sets </h3>

#### Elements of a Set

*  Sets are comprised of members, which are often called ***elements***. 
*  If a particular value ($k$) is an element of set $A$, then we would write this as
\[k \in A \]

*  If a single value $k$ is not an element of set $A$, then we write
\[k \notin A \]



#### Proper Subsets
Given two sets $A$ and $B$, the set $A$ is a ***proper subset*** of set $B$ if every element of $A$ is also an element of $B$, but there are elements of set $B$ that are not in set $A$.


We write this mathematically as
\[A \subset B \]


```{r child="Section_03/Set-IntroductionToSet.Rmd"}
```



```{r child="Section_03/Set-SetOperations.Rmd"}
```

```{r child="Section_03/Set-Theory-Tutorial-1.Rmd"}
```

