---
title: "Spanning Trees"
subtitle: "DiscreteMaths.github.io"
output:
  xaringan::moon_reader:
    css: xaringan-themer.css
    lib_dir: libs
    font_size: 20pts
    nature:
      highlightStyle: github
      countIncrementalSlides: false
---

<style type="text/css">
  body{
  font-size: 20pt;
}
</style>

```{r eval=FALSE,include=FALSE}

# CT6 
# - ASI 2005 April Question B - 1
# - ASI 2006 April Question B - 1

```

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(magrittr)
library(knitr)
library(dplyr)
library(janitor)


```

```{r xaringan-themer, include=FALSE, warning=FALSE}
library(xaringanthemer)
style_mono_accent_inverse(
  #base_color = "#4169e1", #)(vvv#TREES
  #background_color = "#E6E6FA",  #TREE
  base_color = "black", #)(
  background_color =  "#DAB1DA",
  text_color="black",
  text_bold_color = "black",
  header_font_google = google_font("Josefin Sans"),
  text_font_google   = google_font("Montserrat", "400", "300i"),
  code_font_google   = google_font("Fira Mono")
)
```
<style> 
  /* Hide page numbers */ .
  remark-slide-number { display: none; } 
</style>

# Set Theory
## The Power Set

<br>
## Discrete Maths for Computer Science Students
<br><br><br><br>
### <tt>DiscreteMaths.github.io</tt>

---

**De Morgan's Laws in Probability**

De Morgan's Laws are fundamental in set theory and have important implications in probability theory. They provide a way to express the complement of the union or intersection of two events.

**1. Complement of the Union:**

* **Statement:** 
   P( (A ∪ B)' ) = P(A' ∩ B') 

* **Interpretation:** 
   The probability that neither event A nor event B occurs is equal to the probability that both event A does not occur *and* event B does not occur.

<p>

**2. Complement of the Intersection:**

* **Statement:**
   P( (A ∩ B)' ) = P(A' ∪ B')

* **Interpretation:**
   The probability that not both A and B occur is equal to the probability that either A does not occur *or* B does not occur (or neither occurs).

---

**Universal Space** - Four Regions: 1,2,3 and 4

```{r echo=FALSE,fig.width=9,fig.height=5}
library(ggplot2)

# Create a data frame for the rectangle

library(ggplot2)

# Create a data frame for the rectangle
rectangle_df <- data.frame(
  xmin = -5, xmax = 8,
  ymin = -3, ymax = 3
)

# Create data frames for the circles and scale them by a factor of 2
circle1_df <- data.frame(
  x = 2 * cos(seq(0, 2 * pi, length.out = 100)),
  y = 2 * sin(seq(0, 2 * pi, length.out = 100))
)

circle2_df <- data.frame(
  x = 2 * cos(seq(0, 2 * pi, length.out = 100)) + 3,
  y = 2 * sin(seq(0, 2 * pi, length.out = 100))
)

# Create the plot with annotations and no axis ticks
p1<- ggplot() +
  geom_rect(data = rectangle_df, aes(xmin = xmin, xmax = xmax, ymin = ymin, ymax = ymax), fill = "lightgreen", color = "black", alpha = 0.5) +
  geom_polygon(data = circle1_df, aes(x = x, y = y), fill = "blue", alpha = 0.5) +
  geom_polygon(data = circle2_df, aes(x = x, y = y), fill = "red", alpha = 0.5) +
  annotate("text", x = -1, y = 0, label = "1", color = "black", size = 7, fontface = "bold") +
  annotate("text", x = 4, y = 0, label = "2", color = "black", size = 7, fontface = "bold") +
  annotate("text", x = 1.5, y = 0, label = "3", color = "black", size = 7, fontface = "bold") +
  annotate("text", x = -4, y = -2, label = "4", color = "black", size = 7, fontface = "bold") +
  annotate("text", x = 0, y = 0, label = "A", color = "blue", size = 9, fontface = "bold") + 
  annotate("text", x = 3, y = 0, label = "B", color = "red", size = 9, fontface = "bold") + 
  theme_minimal() +
  theme(
    axis.title = element_blank(),
    axis.text = element_blank(),
    axis.ticks = element_blank(),
    panel.grid = element_blank()
  ) +
  coord_equal() +
  labs(title = "Events A and B")

p1
```
* **Event $A$** - Regions 1 and 3   (**Event $A^{c}$** - Regions 2 and 4)
<br>
<br>
* **Event $B$** - Regions 2 and 3   (**Event $B^{c}$** - Regions 1 and 4)
<br>
<br>
* $A^{c} \cup B^{c}$ - Regions 1, 2 and 4   
<br>
* $A^{c} \cap B^{c}$ - Region 4
<br>
---

**Law 1**

```{r echo=FALSE,fig.width=6,fig.height=4}
p1

```

* $A \cup B$ - Regions 1, 2  and 3  
* $(A \cup B)^c$ - Region 4

Recall:

* $A^{c} \cap B^{c}$ - Region 4

Therefore:

   $$P( (A \cup B)^c ) = P(A^{c} \cap B^{c})$$ 
---

**Law 2**

```{r echo=FALSE,fig.width=6,fig.height=4}
p1

```

* $A \cap B$ - Region 3 
* $(A \cap B)^{c}$ - Regions 1, 2  and 4  

Recall:
<br>
* $A^{c} \cup B^{c}$ - Regions 1, 2  and 4 

Therefore:

$$P( (A \cap B)^c ) = P(A^{c} \cup B^{c})$$ 

---

**Example:**

Imagine you're flipping a coin twice. 

* **Event A:** Getting heads on the first flip.
* **Event B:** Getting heads on the second flip.
<br>
<br>
* **A ∪ B:** The event that you get heads on at least one of the flips.
* **(A ∪ B)':** The event that you get tails on both flips.
<br>
<br>
* **A':** The event that you get tails on the first flip.
* **B':** The event that you get tails on the second flip.
* **A' ∩ B':** The event that you get tails on both flips.

As you can see, in this case, P( (A ∪ B)' ) = P(A' ∩ B'), illustrating De Morgan's Law for the complement of the union.

---

**Key Takeaways:**

* De Morgan's Laws provide valuable tools for manipulating and simplifying probability expressions.
* They help to express complex events in terms of simpler ones.
* These laws have applications in various areas of probability and statistics, such as set theory, logic, and circuit design.

**Note:**

* These laws can be extended to more than two events.
* They are closely related to the laws of Boolean algebra.

---


---
