Exercises: Series and Summations {data-navmenu="Exercises"}
==================================

Column {.tabset}
-----------------------------

### Work Sheet 1

#### Question 1

Let $s_n = 1 + 3 + 5 + \ldots + (2n-1)$ for $n \in Z^{+}$.\\

[1.] Express $s_n$ using $\sigma$ notation.

[2.] Calculate $s_1$ , $s_2$ and $s_3$.

[3.] Find a recurrence relation which expresses $s_{n+1}$ in terms of $s_n$.


#### Part 1: 
Express $s_n$ using $\sum$ notation.
\[s_n = 1 + 3 + 5 + \ldots + (2n-1) \mbox{   for }n \in Z^{+}\]


\textbf{Part 1}: Express $s_n$ using $\sum$ notation.
\[s_n = 1 + 3 + 5 + \ldots + (2n-1) \mbox{   for }n \in Z^{+}\]



\[ \sum^{k=n}_{k=1} (2k-1) \]


#### Question 2

Calculate $s_1$, $s_2$ and $s_3$.



\[  \sum^{k=n}_{k=1} (2k-1) \]



#### Question 3

Calculate $s_1$, $s_2$ and $s_3$.



\[  \sum^{k=n}_{k=1} (2k-1) \]


[$s_1$]
[$s_2$]
[$s_3$]


#### Question 4

Find the sum of the following geometric series
\[ 3 + 6 + 12 + 24 + \ldots + 3072 \]

<h5> Solution</h5>

* <a href="https://youtu.be/q6cYD8Ohgno">Solution to this exercise</a>

### Worksheet 2

#### Question 1

Find a recurrence relation which expresses $s_{n+1}$ in terms of $s_n$.


#### Arithmetic Progressions

\[ S_n  = {n \over 2} \left[ 2a+(n-1)d \right] \]

Recall $a=11$,$d=2$ and $n=21$

\[ S_n  = {21 \over 2} \left[ (2.11) +[(21-1)2] \right] \]
\[ S_n  = 10.5 \left[ 22 + 40 \right]  = 10.5 \times 62\]
\[ S_n  = 651 \] 


```{r eval=FALSE,echo=FALSE}
#############################################################################################
# HOB book Page 393
```

Find the sum of the arithmetic progression


\[ 11 + 13 + 15 + \ldots + 49 + 51 \]


First recall two useful equations for working with arithmetic progressions.\\
<br>

For the arithmetic sequence $a,(a+d) ,(a+2d), \ldots$


[(i)] $t_n$ is the $n-th$ term of series.\[ t_n= a+(n-1)d \]

[(ii)] $S_n$ is the sum of the first $n$ terms

\[ S_n  = {n \over 2} \left[ 2a+(n-1)d \right] \]




Find the sum of the arithmetic progression
{
\[ 11 + 13 + 15 + \dots + 49 + 51 \]
}

* Note that $a=11$ and $d=2$.
* We need to find out what $n$ (the number of terms) is.
* The last term is $51$.


<br>
* The last term is $51$.
* $t_n$ = 51 = [ 11 + (n-1)2 ] 
* $t_n$ = 51 = 2n + 9
* $n=21$

There are 21 terms in the series.


\[ S_n  = {n \over 2} \left[ 2a+(n-1)d \right] \]

Recall $a=11$,$d=2$ and $n=21$

\[ \phantom{S_n  = {21 \over 2} \left[ (2.11) +[(21-1)2] \right]} \]
\[ \phantom{S_n  = 10.5 \left[ 22 + 40 \right]  = 10.5 \times 62}\]
\[ \phantom{S_n  = 651} \] 

%%- \vspace{-0.8cm}
\[ S_n  = {n \over 2} \left[ 2a+(n-1)d \right] \]

Recall $a=11$,$d=2$ and $n=21$


\[ S_n  = {21 \over 2} \left[ (2.11) +[(21-1)2] \right] \]
\[ S_n  = 10.5 \left[ 22 + 40 \right]  = 10.5 \times 62\]
\[ S_n  = 651 \] 




### Summations

Find $S_n$, the sum of $n$ terms, of the geometric series

\[  2 + \frac{2}{3} + \frac{2}{3^2} + \frac{2}{3^3} +  \ldots + \frac{2}{3^{n-1}} \]

If $S_n$ = 242/81, find the value of $n$.

\[  2 + \frac{2}{3} + \frac{2}{3^2} + \frac{2}{3^3} +  \ldots + \frac{2}{3^{n-1}} \]
\[ \phantom{ 2 \times \left[ 1 + \frac{1}{3} + \frac{1}{3^2} + \frac{1}{3^3} +  \ldots + \frac{1}{3^{n-1}}   \right]  } \]


#### Summation Theorem

\[ \sum^{n}_{r=0} x^r = \frac{x^{n+1}-1}{x-1} \]
\[ \phantom{k \sum^{n}_{r=0} x^r = k \frac{x^{n+1}-1}{x-1}  } \]
\phantom{Here $k=2$ and $x = 1/3$ }

\[  2 + \frac{2}{3} + \frac{2}{3^2} + \frac{2}{3^3} +  \ldots + \frac{2}{3^{n-1}} \]
\[  2 \times \left[ 1 + \frac{1}{3} + \frac{1}{3^2} + \frac{1}{3^3} +  \ldots + \frac{1}{3^{n-1}}   \right] \]

\textbf{Summation Theorem}

\[ \sum^{n}_{r=0} x^r = \frac{x^{n+1}-1}{x-1} \]
\[ k  \sum^{n}_{r=0} x^r  =  k \left( \frac{x^{n+1}-1}{x-1} \right) \]
Here $k=2$ and $x = 1/3$ 

\[ k  \sum^{n}_{r=0} x^r  =  k \left( \frac{x^{n+1}-1}{x-1} \right) \]
Here $k=2$ and $x = 1/3$ 
\[  \phantom{ 2  \sum^{n}_{r=0} (1/3)^r  =  2 \left( \frac{(1/3)^{n+1}-1}{(1/3)-1} \right) } \]


\[ k  \sum^{n}_{r=0} x^r  =  k \left( \frac{x^{n+1}-1}{x-1} \right) \]
Here $k=2$ and $x = 1/3$ 
\[  2  \sum^{n}_{r=0} (1/3)^r  =  2 \left( \frac{(1/3)^{n+1}-1}{(1/3)-1} \right)  = \frac{242}{81} \]

\[2 \left( \frac{(1/3)^{n+1}-1}{(1/3)-1} \right)  = \frac{-3}{4} \left[ (1/3)^{n+1}-1 \right]  = \frac{242}{81} \]

\[ \frac{-3}{4} \left[ (1/3)^{n+1}-1 \right]  = \frac{242}{81} \]

\[  \left[ (1/3)^{n+1}-1 \right]  =  \frac{-4}{3} \times \frac{242}{81} \]


### Geometric Series


\textbf{Important Equations}

* Summation of $n$ terms
{

\[ S_n = \frac{a(1-r)^n}{1-r} \]
}
* Sum to infinity of a geometric series
{

\[ \mbox{ when } 0 < r < 1 : S_{\infty} = \frac{a}{1-r} \]
}



----------------------------------
{Geometric Series}{Example 1}


\[ \frac{1}{2} + \frac{1}{4} + \frac{1}{8} +  \frac{1}{16} +\ldots  \]




- {Summations}

Summation Theorem

\[ \sum^{n}_{r=0} x^r = \frac{x^{n+1}-1}{x-1} \]

Here $x = 1/3$

\[  2 + \frac{2}{3} + \frac{2}{3^2} + \frac{2}{3^3} +  \ldots + \frac{2}{3^{n-1}} \]

```{r eval=FALSE,echo=FALSE}
# HOB book Page 393
```

First recall two useful equations for working with Arithmetic Progressions

For the arithmetic sequence $a,(a+d) ,(a+2d), \ldots$


[(i)] $t_n$ is the $n-th$ term of series = $a+(n-1)d$

[(ii)] $S_n$ is the sum of the first $n$ terms

\[ S_n  = {n \over 2} \left[ 2a+(n-1)d \right] \]

<br>

Find the sum of the arithmetic progression
{
\[ 11 + 13 + 15 + \dots + 49 + 51 \]
}


* $a=11$ and $d=2$
* We need to find out what $n$ (the number of terms) is.
* The last term is $51$

<br>


* The last term is $51$.
* $t_n$ = 51 = [ 11 + (n-1)2 ] 
* $t_n$ = 51 = 2n + 9
* $n=21$

There are 21 terms in the series.

\[ S_n  = {n \over 2} \left[ 2a+(n-1)d \right] \]

Recall $a=11$,$d=2$ and $n=21$


\[ \phantom{S_n  = {21 \over 2} \left[ (2.11) +[(21-1)2] \right]} \]
\[ \phantom{S_n  = 10.5 \left[ 22 + 40 \right]  = 10.5 \times 62}\]
\[ \phantom{S_n  = 651} \] 

<br>


\[ S_n  = {n \over 2} \left[ 2a+(n-1)d \right] \]

Recall $a=11$,$d=2$ and $n=21$


\[ S_n  = {21 \over 2} \left[ (2.11) +[(21-1)2] \right] \]
\[ S_n  = 10.5 \left[ 22 + 40 \right]  = 10.5 \times 62\]
\[ S_n  = 651 \] 



\[ S_n = \frac{a(1-r)^n}{1-r} \]


\[ \mbox{ when } 0 < r < 1 : S_{\infty} = \frac{a}{1-r} \]

#### Geometric Series - Example 1


\[ \frac{1}{2} + \frac{1}{4} + \frac{1}{8} +  \frac{1}{16} +\ldots  \]







