---
title: "Spanning Trees"
subtitle: "DiscreteMaths.github.io"
output:
  xaringan::moon_reader:
    css: xaringan-themer.css
    lib_dir: libs
    font_size: 20pts
    nature:
      highlightStyle: github
      countIncrementalSlides: false
---

<style type="text/css">
  body{
  font-size: 20pt;
}
</style>



```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(magrittr)
library(knitr)
library(dplyr)
library(janitor)


```

```{r xaringan-themer, include=FALSE, warning=FALSE}
library(xaringanthemer)
style_mono_accent_inverse(
  #base_color = "#4169e1", #)(vvv#TREES
  #background_color = "#E6E6FA",  #TREE
  base_color = "black", #)(
  background_color =  "#FDFD96",
  text_color="black",
  text_bold_color = "black",
  header_font_google = google_font("Josefin Sans"),
  text_font_google   = google_font("Montserrat", "400", "300i"),
  code_font_google   = google_font("Fira Mono")
)
```
<style> 
  /* Hide page numbers */ .
  remark-slide-number { display: none; } 
</style>

# Probability
## Cola Brands - Worked Example
<br>
## Discrete Maths for Computer Science Students
<br><br><br><br>
### <tt>DiscreteMaths.github.io</tt>

---

### Cola Brand Preferences

Consider the following probabilities for a survey about beverage preferences among individuals:

* Let $P$ be the event that ***an individual drinks Pepsi*** and $C$ be the event that ***the individual drink Coca Coca***.

* We are told that $\Pr(P) = 0.72$, $\Pr(C) = 0.24$ and $\Pr(P \cap C) = 0.12$.


### Exercises

A. Calculate the probability that an individual drinks both brands? 

B. Calculate the probability that an individual drinks neither brand? 

C. Are $P$ and $C$ mutually exclusive? 

D. Are $P$ and $C$ independent? 



---

### Solution

Let's tackle these probability questions one by one using the given information:

Given:
- $P$ is the event that an individual drinks Pepsi.
- $C$ is the event that an individual drinks Coca-Cola.
- $\Pr(P) = 0.72$
- $\Pr(C) = 0.24$
- $\Pr(P \cap C) = 0.12$


---

### Exercise A. 

**Calculate the probability that an individual drinks both brands**

* The probability that an individual drinks both brands is given by:

$$\Pr(P \cap C) = 0.12$$

---

### Exercise B. 

**Calculate the probability that an individual drinks neither brand**

* The probability of an individual drinking neither brand can be found by using the complement rule. 

* First, we find the probability that an individual drinks at least one of the brands:

$$\Pr(P \cup C) = \Pr(P) + \Pr(C) - \Pr(P \cap C)$$

$$\Pr(P \cup C) = 0.72 + 0.24 - 0.12 = 0.84$$

* So, the probability that an individual drinks neither brand is:
$$\Pr(\text{neither } P \text{ nor } C) = 1 - \Pr(P \cup C) = 1 - 0.84
= 0.16$$

---

### Exercise C. 

**Are $P$ and $C$ mutually exclusive?**

* Two events are mutually exclusive if they cannot occur at the same time, i.e., $\Pr(P \cap C) = 0$.

* Given that:
$$\Pr(P \cap C) = 0.12$$

* Since $\Pr(P \cap C) \neq 0$, the events $P$ and $C$ are not mutually exclusive.

---

### Exercise D. 

**Are $P$ and $C$ independent?**

* Two events are independent if the occurrence of one does not affect the probability of the other. 

Mathematically, $P$ and $C$ are independent if:

$$\Pr(P \cap C) = \Pr(P) \times \Pr(C)$$

* Recall: $\Pr(P) = 0.72$, $\Pr(C) = 0.24$ and $\Pr(P \cap C) = 0.12$

* Calculate $\Pr(P) \times \Pr(C)$:
$$\Pr(P) \times \Pr(C) = 0.72 \times 0.24 = 0.1728$$

* Since:
$$\Pr(P \cap C) = 0.12 \neq 0.1728$$

* The events $P$ and $C$ are not independent.

---

### Summary:

- **A.** The probability that an individual drinks both brands: $\Pr(P \cap C) = 0.12$

- **B.** The probability that an individual drinks neither brand: $0.16$

- **C.** $P$ and $C$ are not mutually exclusive.

- **D.** $P$ and $C$ are not independent.

---

---