---
title: "Spanning Trees"
subtitle: "DiscreteMaths.github.io"
output:
  xaringan::moon_reader:
    css: xaringan-themer.css
    lib_dir: libs
    font_size: 20pts
    nature:
      highlightStyle: github
      countIncrementalSlides: false
---

<style type="text/css">
  body{
  font-size: 20pt;
}
</style>



```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(magrittr)
library(knitr)
library(dplyr)
library(janitor)


```

```{r xaringan-themer, include=FALSE, warning=FALSE}
library(xaringanthemer)
style_mono_accent_inverse(
  #base_color = "#4169e1", #)(vvv#TREES
  #background_color = "#E6E6FA",  #TREE
  base_color = "black", #)(
  background_color =  "#FDFD96",
  text_color="black",
  text_bold_color = "black",
  header_font_google = google_font("Josefin Sans"),
  text_font_google   = google_font("Montserrat", "400", "300i"),
  code_font_google   = google_font("Fira Mono")
)
```
<style> 
  /* Hide page numbers */ .
  remark-slide-number { display: none; } 
</style>

# Probability
## Sampling From Two Urns - Sample Space
<br>
## Discrete Maths for Computer Science Students
<br><br><br><br>
### <tt>DiscreteMaths.github.io</tt>

---

### Sampling From Two Urns

Suppose one urn contains three balls: one red, one blue, and one green, and a second urn contains three balls numbered 1, 2, and 3. 

An experiment consists of two balls being drawn at random (i.e. one from each urn).


### Exercise 

Write out the sample space for this experiment.

---

***First Urn***:  one red, one blue, and one green

***Second urn***: three balls numbered 1, 2, and 3. 

An experiment consists of two balls being drawn at random (i.e., one from each urn).


- $R$ represents the red ball from the first urn

- $B$ represents the blue ball from the first urn

- $G$ represents the green ball from the first urn

- $1, 2, 3$ represent the numbered balls from the second urn

**Sample Space**:

The sample space consists of all possible combinations of drawing one ball from each urn.

$$S = \{ (R,1), (R,2), (R,3), (B,1), (B,2), (B,3), (G,1), (G,2), (G,3) \}$$


---


---