---
title: "Spanning Trees"
subtitle: "DiscreteMaths.github.io"
output:
  xaringan::moon_reader:
    css: xaringan-themer.css
    lib_dir: libs
    font_size: 20pts
    nature:
      highlightStyle: github
      countIncrementalSlides: false
---

<style type="text/css">
  body{
  font-size: 20pt;
}
</style>



```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(magrittr)
library(knitr)
library(dplyr)
library(janitor)


```

```{r xaringan-themer, include=FALSE, warning=FALSE}
library(xaringanthemer)
style_mono_accent_inverse(
  #base_color = "#4169e1", #)(vvv#TREES
  #background_color = "#E6E6FA",  #TREE
  base_color = "black", #)(
  background_color =  "#FDFD96",
  text_color="black",
  text_bold_color = "black",
  header_font_google = google_font("Josefin Sans"),
  text_font_google   = google_font("Montserrat", "400", "300i"),
  code_font_google   = google_font("Fira Mono")
)
```
<style> 
  /* Hide page numbers */ .
  remark-slide-number { display: none; } 
</style>

# Probability
## Picking Beads From An Urn (Worked Example)
<br>
## Discrete Maths for Computer Science Students
<br><br><br><br>
### <tt>DiscreteMaths.github.io</tt>

---

### Sampling from an Urn

Suppose an urn contains seven white, four black, and three red beads. 

Three beads are picked at random without replacement. 


### Exercises

Find the probability that:

A. All three beads are of different colors.

B. At least two beads are the same color.

---

## Sampling from an Urn

### Exercise A.

**Probability that all three beads are of different colors**

1. **Total number of ways to pick 3 beads out of 14**:
$$\binom{14}{3} = \frac{14!}{3!(14-3)!} = \frac{14 \times 13 \times 12}{3 \times 2 \times 1} = 364$$

2. **Number of ways to pick 1 white, 1 black, and 1 red**:
$$\binom{7}{1} \times \binom{4}{1} \times \binom{3}{1} = 7 \times 4 \times 3 = 84$$

3. **Probability**:
$$P(\text{all three beads are different}) = \frac{84}{364} \approx 0.2308$$


---

### Exercise B.

**Probability that at least two beads are the same color**

We can find this by using the complement rule. First, calculate the probability that all three beads are of different colors (which we found above) and then subtract it from 1:

$$P(\text{at least 2 beads are the same}) = 1 - P(\text{all three beads are different})$$
$$P(\text{at least 2 beads are the same}) = 1 - 0.2308 \approx 0.7692$$

---