---
title: "Spanning Trees"
subtitle: "DiscreteMaths.github.io"
output:
  xaringan::moon_reader:
    css: xaringan-themer.css
    lib_dir: libs
    font_size: 20pts
    nature:
      highlightStyle: github
      countIncrementalSlides: false
---

<style type="text/css">
  body{
  font-size: 20pt;
}
</style>

```{r eval=FALSE,include=FALSE}

# CT6 
# - ASI 2005 April Question B - 1
# - ASI 2006 April Question B - 1

```

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(magrittr)
library(knitr)
library(dplyr)
library(janitor)


```

```{r xaringan-themer, include=FALSE, warning=FALSE}
library(xaringanthemer)
style_mono_accent_inverse(
  #base_color = "#4169e1", #)(vvv#TREES
  #background_color = "#E6E6FA",  #TREE
  base_color = "black", #)(
  background_color =  "#FFA756",
  text_color="black",
  text_bold_color = "black",
  header_font_google = google_font("Josefin Sans"),
  text_font_google   = google_font("Montserrat", "400", "300i"),
  code_font_google   = google_font("Fira Mono")
)
```
<style> 
  /* Hide page numbers */ .
  remark-slide-number { display: none; } 
</style>

# Counting Problems
### Character Counting in an Alphabet of Five Symbols


<br>
## Discrete Maths for Computer Science Students
<br><br><br><br>
### <tt>DiscreteMaths.github.io</tt>

---

### Counting Problem

* A string is a palindrome if the string is the same when we read it from the left and from the right, for example: tacocat. 

* Let the alphabet be the symbols {a,b,c,d,e}. 

* How many palindromes of length 11 exists over this alphabet?


---

### Solution

To solve the problem of finding the number of palindromes of length 11 over the alphabet {a, b, c, d, e}, we can follow this solution:

1. A string is a palindrome if it reads the same forwards and backwards.
2. A palindrome of length 11 can be written in the form $s x \overline{s}$, 
  - where $s$ is a string of length 5, 
  - $x$ is a single symbol, 
  - and $\overline{s}$ is the reverse of $s$.

$${\Large{ \underline{a,b,c,d,a},\mid\textbf{e}\mid,\overline{ a, d,c,b,a, } } }$$
---

### Steps:
- Let $s$ be a string of length 5. Each position in $s$ can be filled with any of the 5 symbols from the alphabet {a, b, c, d, e}.
- Since $s$ has 5 positions, and each position has 5 choices, there are $5^5$ possible strings for $s$.
- The single symbol $x$ also has 5 choices.

<br>

### Completing the Palindrome
For a palindrome of length 11, the 7th, 8th, and 9th positions are essentially determined by the 5th, 4th, and 3rd positions, respectively, because the string reads the same forwards and backwards.

In this case, there are no independent choices for the 7th, 8th, and 9th positions because their values are dictated by the corresponding earlier positions to ensure the palindrome property.

---

### Calculation:
- The total number of palindromes is given by:
$$5^5 \times 5 = 5^6$$

- Calculating $5^6$:
$$5^6 = 15625$$
  
<br>

### Conclusion:
There are 15,625 different palindromes of length 11 over the alphabet {a, b, c, d, e}.

---

---