---
title: "Spanning Trees"
subtitle: "DiscreteMaths.github.io"
output:
  xaringan::moon_reader:
    css: xaringan-themer.css
    lib_dir: libs
    font_size: 20pts
    nature:
      highlightStyle: github
      countIncrementalSlides: false
---

<style type="text/css">
  body{
  font-size: 20pt;
}
</style>



```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(magrittr)
library(knitr)
library(dplyr)
library(janitor)


```

```{r xaringan-themer, include=FALSE, warning=FALSE}
library(xaringanthemer)
style_mono_accent_inverse(
  #base_color = "#4169e1", #)(vvv#TREES
  #background_color = "#E6E6FA",  #TREE
  base_color = "black", #)(
  background_color =  "#FDFD96",
  text_color="black",
  text_bold_color = "black",
  header_font_google = google_font("Josefin Sans"),
  text_font_google   = google_font("Montserrat", "400", "300i"),
  code_font_google   = google_font("Fira Mono")
)
```
<style> 
  /* Hide page numbers */ .
  remark-slide-number { display: none; } 
</style>

# Probability
## Students Hair Colour (Worked Example)
<br>
## Discrete Maths for Computer Science Students
<br><br><br><br>
### <tt>DiscreteMaths.github.io</tt>

---

### Hair Colour

In a class of 20 pupils, 11 have dark hair, 7 have fair hair, and 2 have red hair. Two pupils are chosen at random to collect the homework.

### Exercise

What is the probability that:

A. Both have fair hair

B. Each has hair of a different color


---

### Solution

**Probability questions about pupils with different hair colors**

Let's denote:
- $D$ for pupils with dark hair ($11$ pupils)
- $F$ for pupils with fair hair ($7$ pupils)
- $R$ for pupils with red hair ($2$ pupils)

Two pupils are chosen at random to collect the homework.

---

### Exercise A.

**Probability that both pupils have fair hair**

* The number of ways to choose 2 fair-haired pupils out of 7 is:
$$\binom{7}{2} = \frac{7!}{2!(7-2)!} = \frac{7 \times 6}{2 \times 1} = 21$$

* The total number of ways to choose 2 pupils out of 20 is:
$$\binom{20}{2} = \frac{20!}{2!(20-2)!} = \frac{20 \times 19}{2 \times 1} = 190$$

* The probability that both pupils have fair hair is:
$$P(\text{both have fair hair}) = \frac{\binom{7}{2}}{\binom{20}{2}} = \frac{21}{190} = \frac{21}{190} \approx 0.1105$$

---
### Exercise B 

**Probability that each pupil has a different hair color**

The number of ways to choose 2 pupils with different hair colors can be found by summing the combinations of pupils with different hair colors:

- Choosing 1 dark-haired and 1 fair-haired:
$$\binom{11}{1} \times \binom{7}{1} = 11 \times 7 = 77$$

- Choosing 1 dark-haired and 1 red-haired:
$$\binom{11}{1} \times \binom{2}{1} = 11 \times 2 = 22$$

- Choosing 1 fair-haired and 1 red-haired:
$$\binom{7}{1} \times \binom{2}{1} = 7 \times 2 = 14$$
---

### Exercise B 

Total number of ways to choose 2 pupils with different hair colors:
$$77 + 22 + 14 = 113$$

The probability that each pupil has a different hair color is:
$$P(\text{different hair color}) = \frac{113}{190} = \frac{113}{190} \approx 0.5947$$

---

---