---
title: "Spanning Trees"
subtitle: "DiscreteMaths.github.io"
output:
  xaringan::moon_reader:
    css: xaringan-themer.css
    lib_dir: libs
    font_size: 20pts
    nature:
      highlightStyle: github
      countIncrementalSlides: false
---

<style type="text/css">
  body{
  font-size: 20pt;
}
</style>



```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(magrittr)
library(knitr)
library(dplyr)
library(janitor)


```

```{r xaringan-themer, include=FALSE, warning=FALSE}
library(xaringanthemer)
style_mono_accent_inverse(
  #base_color = "#4169e1", #)(vvv#TREES
  #background_color = "#E6E6FA",  #TREE
  base_color = "black", #)(
  background_color =  "#FDFD96",
  text_color="black",
  text_bold_color = "black",
  header_font_google = google_font("Josefin Sans"),
  text_font_google   = google_font("Montserrat", "400", "300i"),
  code_font_google   = google_font("Fira Mono")
)
```
<style> 
  /* Hide page numbers */ .
  remark-slide-number { display: none; } 
</style>

# Probability
## Winning the National Lottery
<br>
## Discrete Maths for Computer Science Students
<br><br><br><br>
### <tt>DiscreteMaths.github.io</tt>

---
### National Lottery:

In the National Lottery 6 numbers are chosen without replacement from 49. 

### Exercises
Calculate the probability of 

A. winning the jackpot (choosing all 6 numbers correctly)

B. winning the smallest prize (choosing 3 of the 6 numbers correctly)

C. choosing at least one of the numbers correctly.




---

### Exercise A.

**Winning the Jackpot (choosing all 6 numbers correctly)**

* The total number of ways to choose 6 numbers out of 49 is given by the combination formula:
$$\binom{49}{6} = \frac{49!}{6!(49-6)!}$$

* Calculating this:
$$\binom{49}{6} = \frac{49!}{6!43!} = 13,983,816$$

* Since there is only one correct combination out of the 13,983,816 possibilities:
$$P(\text{winning the jackpot}) = \frac{1}{13,983,816}$$

---

### Exercise B.

**Winning the Smallest Prize (choosing 3 of the 6 numbers correctly)**

* For winning the smallest prize, you need to choose 3 correct numbers out of the 6 winning numbers and 3 incorrect numbers out of the 43 remaining numbers.

* The number of ways to choose 3 correct numbers out of 6:
$$\binom{6}{3} = 20$$

* The number of ways to choose 3 incorrect numbers out of 43:
$$\binom{43}{3} = 12,341$$

* The total number of ways to choose 3 correct and 3 incorrect numbers:
$$\binom{6}{3} \times \binom{43}{3} = 20 \times 12,341 = 246,820$$

---

### Exercise B.

* The probability of winning the smallest prize:

$$P(\text{winning the smallest prize}) = \frac{246,820}{13,983,816} \approx 0.01765$$

---

### Exercise C.

**Choosing at Least One of the Numbers Correctly**

* The probability of choosing at least one correct number is the complement of the probability of choosing none of the correct numbers.

* The number of ways to choose 6 incorrect numbers out of 43:
$$\binom{43}{6} = \frac{43!}{6!37!} = 4,496,388$$

* The probability of choosing none of the correct numbers:
$$P(\text{choosing none correctly}) = \frac{4,496,388}{13,983,816} \approx 0.321$$

* Therefore, the probability of choosing at least one correct number:

$$P(\text{choosing at least one correctly}) = 1 - P(\text{choosing none correctly})$$

$$P(\text{choosing at least one correctly}) \approx 1 - 0.321 = 0.679$$

---

---
