---
title: "Spanning Trees"
subtitle: "DiscreteMaths.github.io"
output:
  xaringan::moon_reader:
    css: xaringan-themer.css
    lib_dir: libs
    font_size: 20pts
    nature:
      highlightStyle: github
      countIncrementalSlides: false
---

<style type="text/css">
  body{
  font-size: 20pt;
}
</style>



```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(magrittr)
library(knitr)
library(dplyr)
library(janitor)


```

```{r xaringan-themer, include=FALSE, warning=FALSE}
library(xaringanthemer)
style_mono_accent_inverse(
  #base_color = "#4169e1", #)(vvv#TREES
  #background_color = "#E6E6FA",  #TREE
  base_color = "black", #)(
  background_color =  "#FF964F",
  text_color="black",
  text_bold_color = "black",
  header_font_google = google_font("Josefin Sans"),
  text_font_google   = google_font("Montserrat", "400", "300i"),
  code_font_google   = google_font("Fira Mono")
)
```
<style> 
  /* Hide page numbers */ .
  remark-slide-number { display: none; } 
</style>

# Counting Problems
##  Principle of Inclusion and Exclusion
<br>
## Discrete Maths for Computer Science Students
<br><br><br><br>
### <tt>DiscreteMaths.github.io</tt>

---

## Principle of Inclusion and Exclusion

### School Example 

* Among a group of students, 50 played cricket, 50 played hockey and 40 played volley ball. 

* 15 played both cricket and hockey, 20 played both hockey and volley ball, 15 played cricket and volley ball and 10 played all three. 

* If every student played at least one game, find the number of students and how many played only cricket, only hockey and only volley ball?



---

### Definitions:

- Let $C$ be the set of students who played cricket.

- Let $H$ be the set of students who played hockey.

- Let $V$ be the set of students who played volleyball.


We are given the following:
- $|C| = 50$ (students who played cricket)

- $|H| = 50$ (students who played hockey)

- $|V| = 40$ (students who played volleyball)

- $|C \cap H| = 15$ (students who played both cricket and hockey)

- $|H \cap V| = 20$ (students who played both hockey and volleyball)

- $|C \cap V| = 15$ (students who played both cricket and volleyball)

- $|C \cap H \cap V| = 10$ (students who played all three games)


---

## Principle of Inclusion and Exclusion

The principle of inclusion and exclusion is a fundamental concept in counting problems used to calculate the size of the union of multiple sets. 

This principle helps to avoid overcounting elements that belong to multiple sets by systematically including and excluding the intersections of these sets.

### Explanation:

For two sets $A$ and $B$:
$$|A \cup B| = |A| + |B| - |A \cap B|$$

- $|A|$ is the number of elements in set $A$.
- $|B|$ is the number of elements in set $B$.
- $|A \cap B|$ is the number of elements that are in both $A$ and $B$.

---

### For Three Sets:

For three sets $A$, $B$, and $C$:
$$|A \cup B \cup C| = |A| + |B| + |C| - |A \cap B| - |A \cap C| - |B \cap C| + |A \cap B \cap C|$$

- We add the sizes of the individual sets $|A|$, $|B|$, and $|C|$.
- We subtract the sizes of the pairwise intersections $|A \cap B|$, $|A \cap C|$, and $|B \cap C|$ to correct for double counting.
- We add back the size of the intersection of all three sets $|A \cap B \cap C|$ to correct for triple counting.

---

### Total Number of Students:
The total number of students is given by the principle of inclusion and exclusion:

$$|C \cup H \cup V| = |C| + |H| + |V| - |C \cap H| - |H \cap V| - |C \cap V| + |C \cap H \cap V|$$

Substituting the given values:

$$
|C \cup H \cup V| = 50 + 50 + 40 - 15 - 20 - 15 + 10 = 100
$$

So, the total number of students is $100$.

---

### Number of Students Who Played Only One Game:

To find the number of students who played only one game, we subtract those who played multiple games from the total number who played each game.



**Only Cricket**:

$$
|C_{\text{only}}| = |C| - |C \cap H| - |C \cap V| + |C \cap H \cap V|
$$

Substituting the given values:

$$
|C_{\text{only}}| = 50 - 15 - 15 + 10 = 30
$$

---

### Number of Students Who Played Only One Game:

**Only Hockey**:

$$
|H_{\text{only}}| = |H| - |H \cap C| - |H \cap V| + |C \cap H \cap V|
$$

Substituting the given values:

$$
|H_{\text{only}}| = 50 - 15 - 20 + 10 = 25
$$

<br>

**Only Volleyball**:

$$
|V_{\text{only}}| = |V| - |V \cap C| - |V \cap H| + |C \cap H \cap V|
$$

Substituting the given values:

$$
|V_{\text{only}}| = 40 - 15 - 20 + 10 = 15
$$

---

### Summary:
- The total number of students is $100$.
- The number of students who played only cricket is $30$.
- The number of students who played only hockey is $25$.
- The number of students who played only volleyball is $15$.

---