Yes, there are several R packages well-suited for graph visualization for undergraduate computer science students:

**1. igraph**

*   A powerful and comprehensive package for graph analysis and visualization.
*   Supports various graph data structures (directed, undirected, weighted).
*   Offers a wide range of graph algorithms (e.g., shortest paths, community detection).
*   Includes functions for plotting graphs with customizable layouts and aesthetics.

**2. ggraph**

*   A grammar-of-graphics approach to graph visualization, built on top of ggplot2.
*   Provides a flexible and elegant way to create visually appealing and informative graph plots.
*   Integrates well with other ggplot2 extensions for advanced customization.

**3. visNetwork**

*   Creates interactive and web-based network visualizations using the JavaScript library vis.js.
*   Allows for interactive exploration of graphs, such as node dragging, zooming, and filtering.
*   Suitable for creating dynamic and engaging visualizations.

**Example (Using igraph):**

```R
library(igraph)

# Create a graph
g <- graph_from_edgelist(matrix(c(1, 2, 1, 3, 2, 3, 2, 4, 3, 4), ncol = 2, byrow = TRUE))

# Plot the graph
plot(g, vertex.size = 40, vertex.label = V(g)) 
```

These packages provide excellent tools for visualizing graphs in R. Choose the one that best suits your specific needs and preferences based on the level of customization, interactivity, and integration with other R packages that you require.

I hope this helps!
