```R
# Install and load necessary packages
install.packages("VennDiagram")
library(VennDiagram)

# Define sets 
set1 <- c("A", "B", "C", "D")
set2 <- c("B", "C", "E", "F")
set3 <- c("C", "D", "F", "G")

# Create a list of sets
list_sets <- list(set1, set2, set3)

# Create the Venn diagram
venn.diagram(
  x = list_sets,
  category.names = c("Set 1", "Set 2", "Set 3"),
  filename = "venn_diagram.png", 
  # Optional: Customize appearance
  fill = c("lightblue", "pink", "lightgreen"),
  alpha = 0.5, 
  cex = 1.2,
  cat.cex = 1.5,
  cat.fontfamily = "sans serif"
) 
```

**Explanation:**

1. **Install and Load Packages:**
   - `install.packages("VennDiagram")`: Installs the necessary package.
   - `library(VennDiagram)`: Loads the package into your R session.

2. **Define Sets:**
   - Create vectors representing your sets. In this example, `set1`, `set2`, and `set3` contain sample elements.

3. **Create a List of Sets:**
   - Combine the sets into a list using `list(set1, set2, set3)`. This list will be used as input for the `venn.diagram()` function.

4. **Create the Venn Diagram:**
   - `venn.diagram()`: This is the main function for creating Venn diagrams.
      - `x`: The list of sets.
      - `category.names`: A vector of names for each set.
      - `filename`: The name of the file to save the diagram to (e.g., "venn_diagram.png").
      - **Customization Options:**
         - `fill`: Colors to fill each set region.
         - `alpha`: Transparency level for the fill colors.
         - `cex`: Font size for the numbers within the diagram.
         - `cat.cex`: Font size for the set labels.
         - `cat.fontfamily`: Font family for the set labels.

**Key Points:**

* This code creates a basic Venn diagram for three sets. You can adjust the sets, colors, and other parameters to customize the diagram.
* The `VennDiagram` package offers various options for customizing the appearance of the diagram, such as adding borders, changing font styles, and adjusting the size of the plot.
* You can use this approach to create Venn diagrams for two, three, or even more sets.

This example provides a basic framework for creating Venn diagrams in R. You can explore the `VennDiagram` package documentation for more advanced customization options and features.
